### 2014-09-21 Template/iwslt2014-submission.tex
.

\documentclass[a4paper]{article}
\usepackage{iwslt14,amssymb,amsmath,epsfig}
\setcounter{page}{1}
\sloppy		% better line breaks
%\ninept
%SM below a registered trademark definition
\def\reg{{\rm\ooalign{\hfil
     \raise.07ex\hbox{\scriptsize R}\hfil\crcr\mathhexbox20D}}}

%% \newcommand{\reg}{\textsuperscript{\textcircled{\textsc r}}}

\title{Paper Template for IWSLT 2014}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Please make sure to keep technical paper submissions anonymous  !
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\name{Firstname Lastname}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If multiple authors, uncomment and edit the lines shown below.       %%
%% Note that each line must be emphasized {\em } by itself.             %%
%% (by Stephen Martucci, author of spconf.sty).                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \makeatletter
% \def\name#1{\gdef\@name{#1\\}}
% \makeatother
% \name{{\em Firstname1 Lastname1, Firstname2 Lastname2, Firstname3 Lastname3,}\\
%      {\em Firstname4 Lastname4}}
%%%%%%%%%%%%%%% End of required multiple authors changes %%%%%%%%%%%%%%%%%

\address{Department of Speech Recognition and Machine Translation  \\
University of SomePlace, SomeCountry \\
{\small \tt firstname.lastname@iwslt.org}
}
%
\begin{document}
\maketitle
%
\begin{abstract}
This is a layout specification and template
definition for the paper of the IWSLT 2014 Conference. 
The format is essentially the one used for the IEEE ICASSP conferences.
\end{abstract}

%
\section{Introduction}
This template can be found on the conference 
website: \texttt{http://workshop2014.iwslt.org/}.
Please use either a MS-Word\reg\ or a \LaTeX\ format file
when preparing your submission.

\section{Page layout and style}

Authors should should observe the following rules for page
layout. A highly  recommended way to meet these requirements
is to use a predefined template and check
details against the corresponding example file.

\subsection{First page}

The first page should have the paper title, author(s), and affiliation(s)
centered on the page across both columns. The remainder of the text 
must be in the two-column format, staying within the indicated image 
area.

\subsubsection{Paper Title}
The paper title must be in boldface. All non-function words must be capitalized,
and all other words in the title must be lower case. The paper title is centered
across the top of the two columns on the first page as indicated above.

\subsubsection{Authors' Name(s)}
The authors' name(s) and affiliation(s) appear centered below the paper
title. If space permits, include a mailing address here. The templates indicate
the area where the title and author information should go. These items need not
be confined to the number of lines indicated; papers with multiple
authors and affiliations may require two or more lines. 
Note that the submission version of technical papers \emph{should be 
anonymized for review}.

\subsubsection{Abstract}
Each paper must contain an abstract that appears at the beginning of the paper.

\subsection{Basic layout features}

\begin{itemize}
%\itemsep -1.3mm
\item Proceedings will be printed in A4 format. The layout is designed 
so that files, when printed in US Letter format, include all material 
but margins are not symmetric. 
Although this is not an absolute requirement, if at all possible,
{\bf PLEASE TRY TO MAKE YOUR SUBMISSION IN A4 FORMAT.}
\item Two columns are used except for the title part and possibly for large 
figures that need a full page width.
\item Left margin is 20 mm.
\item Column width is 80 mm.
\item Spacing between columns is 10 mm.
\item Top margin 25 mm (except first page 30 mm to title top).
\item Text height (without headers and footers) is maximum 235 mm.
\item Headers and footers must be left empty (they will be added for 
printing).
\item Check indentations and spacings by comparing to this 
example file (in pdf format).
\end{itemize}

\subsubsection{Headings}

Section headings are centered in boldface
with the first word capitalized and the rest of the heading in 
lower case. Sub-headings appear like major headings, except they 
start at the left margin in the column.
Sub-sub-headings appear like sub-headings, except they are in italics 
and not boldface. See the examples given in this 
file. No more than 3 levels of headings should be used.

\subsection{Text font}

Times or Times Roman font is used for the main text. Recommended 
font size is 9 points which is also the minimum allowed size.
Other font types may be used if needed for 
special purposes. While making the final PostScript file, 
remember to include all fonts!

\LaTeX\ users: DO NOT USE Computer Modern FONT FOR TEXT (Times is 
specified in the style file). If possible, make the final 
document using POSTSCRIPT FONTS.
This is necessary given that, for example, equations with 
non-ps Computer Modern are very hard to read on screen.

\subsection{Figures}

All figures must be centered on the column (or page, if the figure spans 
both columns).
Figure captions should follow each figure and have the format given in 
Fig.~\ref{spprod}.

Figures should preferably be line drawings. If they contain gray 
levels or colors, they should be checked to print well on a 
high-quality non-color laser printer.

\subsection{Tables}

An example of a table is shown as Table \ref{table1}. Somewhat 
different styles are allowed according to the type and purpose of the 
table. The caption text may be above or below the table.

\begin{table} [t,h]
\caption{\label{table1} {\it This is an example of a table.}}
\vspace{2mm}
\centerline{
\begin{tabular}{|c|c|}
\hline
ratio & decibels \\
\hline  \hline
1/1 & 0 \\
2/1 & $\approx 6$ \\
3.16 & 10 \\
10/1 & 20 \\ 
1/10 & -20 \\
\hline
\end{tabular}}
\end{table}

\subsection{Equations}

Equations should be placed on separate lines and numbered. Examples 
of equations are given below.
Particularly,
%
%\vspace{-3mm}
\begin{equation}
x(t) = s(f_\omega(t))
\label{eq1}
\end{equation}
where \(f_\omega(t)\) is a special warping function
\begin{equation}
f_\omega(t)=\frac{1}{2\pi j}\oint_C \frac{\nu^{-1k}d\nu}
{(1-\beta\nu^{-1})(\nu^{-1}-\beta)}
\label{eq2}
\end{equation}
A residue theorem states that
\begin{equation}
\oint_C F(z)dz=2 \pi j \sum_k Res[F(z),p_k]
\label{eq3}
\end{equation}
Applying (\ref{eq3}) to (\ref{eq1}), 
it is straightforward to see that
\begin{equation}
1 + 1 = \pi
\label{eq4}
\end{equation}

Make sure to use \verb!\eqref! when refering to equation numbers.
Finally we have proven the secret theorem of all speech sciences (see
equation~\eqref{eq3} above).  No more math is needed to show how 
useful the result is!

\begin{figure}[t]
\centerline{\epsfig{figure=figure,width=40mm}}
\caption{{\it Schematic diagram of speech production.}}  
\label{spprod}
\end{figure}

\subsection{Hyperlinks}

Hyperlinks can be included in your paper. Moreover, be aware that the paper
submission procedure includes the option of specifying a hyperlink for
additional information.  This hyperlink will be included in the CD-ROM.
Particularly pay attention to the possibility, from this single hyperlink, to
have further links to information such as other related documents, sound or
multimedia.

If you choose to use active hyperlinks in your paper, 
please make sure that they present no problems in printing to paper.

\subsection{Page numbering}

Final page numbers will be added later to the document
electronically. 
{\em Please don't make any headers or footers!}.

\subsection{References}

The reference format is the standard for IEEE publications.
References should be numbered in order of appearance, 
for example \cite{ES1}, \cite{ES2}, and \cite{ES3}.

\section{Experiments}
Please make sure to give all the necessary details regarding your experimental 
setting so as to ensure that your results could be reproduced by other teams.

\section{Conclusions}

This paper has described a novel approach for doing wonderful stuff such as ...

\section{Acknowledgements}
The IWSLT 2014 organizing committee would like to thank the
organizing committees of INTERSPEECH 2004 for their
help and for kindly providing the template files.

%
\bibliographystyle{IEEEtran}
\begin{thebibliography}{10}
\bibitem[1]{ES1} Smith, J. O. and Abel, J. S., 
``Bark and {ERB} Bilinear Transforms'', 
IEEE Trans. Speech and Audio Proc., 7(6):697--708, 1999.  
\bibitem[2]{ES2} Lee, K.-F., Automatic Speech Recognition: 
The Development of the 
SPHINX SYSTEM, Kluwer Academic Publishers, Boston, 1989.
\bibitem[3]{ES3} Rudnicky, A. I., Polifroni, Thayer, E. H.,
 and Brennan, R. A.  
"Interactive problem solving with speech", J. Acoust. Soc. Amer., 
Vol. 84, 1988, p S213(A).
\end{thebibliography}
\end{document}

### 2014-09-22 Paper/paper.tex
.

--- 2014-09-21 Template/iwslt2014-submission.tex
@@
 
-\title{Paper Template for IWSLT 2014}
+\title{Rule-Based Preordering on
+Multiple Syntactic Levels in
+Statistical Machine Translation}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\name{Firstname Lastname}
+%\name{Firstname Lastname}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \makeatletter
-% \def\name#1{\gdef\@name{#1\\}}
-% \makeatother
-% \name{{\em Firstname1 Lastname1, Firstname2 Lastname2, Firstname3 Lastname3,}\\
-%      {\em Firstname4 Lastname4}}
+ \makeatletter
+ \def\name#1{\gdef\@name{#1\\}}
+ \makeatother
+ \name{{\em Ge Wu, Yuqi Zhang}}
 %%%%%%%%%%%%%%% End of required multiple authors changes %%%%%%%%%%%%%%%%%
 
-\address{Department of Speech Recognition and Machine Translation  \\
-University of SomePlace, SomeCountry \\
-{\small \tt firstname.lastname@iwslt.org}
+\address{Institute for Anthropomatics \\
+Karlsruhe Institute of Technoloy, Germany \\
+{\small \tt utcur@student.kit.edu, yuqi.zhang@kit.edu}
 }
@@
 \begin{abstract}
-This is a layout specification and template
-definition for the paper of the IWSLT 2014 Conference. 
-The format is essentially the one used for the IEEE ICASSP conferences.
+We propose a novel data-driven rule-based preordering approach, which uses the information of syntax tree and word alignment to reorder the words in source sentences before decoding in a phrase-based SMT system between English and Chinese.
+The preorering algorithm extracts reordering patterns from multiple levels of the syntax trees of the training data and applies the rules on the source sentences in a similar manner.
+We've conducted experiments in English-to-Chinese and Chinese-to-English translation directions.
+Our results show that the approach has led to improved translation quality both when it was applied separately on the baseline or when it was combined with some other reordering approaches.
+We report an improvement of $0.43$ in BLEU score when our preordering approach was used in addition to the short rule \cite{short}, long rule\cite{long} and tree rule \cite{tree} based preordering approaches in the English-to-Chinese translation direction.
+There's also an improvement of $0.3$ in BLEU score when our preordering approach was used in addition to the aforementioned preordering approaches in the Chinese-to-English translation direction.
+Through the translation examples, we've also found improvements in syntactic structure with our preordering approach.
 \end{abstract}
-
 %
 \section{Introduction}
-This template can be found on the conference 
-website: \texttt{http://workshop2014.iwslt.org/}.
-Please use either a MS-Word\reg\ or a \LaTeX\ format file
-when preparing your submission.
 
-\section{Page layout and style}
+Word order is a general issue when we want to translate text from one language to the other.
+Different languages normally have different word orders and the difference could be very huge.
+Among all the languages, Chinese is one language which is very different from English, because they belong to different language families and have long period of separately development.
+Both languages have a Subject-Verb-Object order, but they also have a lot of differences in word order.
+Especially sentences in both languages can sometimes have completely different syntactic structures.
+The differences may involve long-distance or unstructured position changes.
 
-Authors should should observe the following rules for page
-layout. A highly  recommended way to meet these requirements
-is to use a predefined template and check
-details against the corresponding example file.
+Most state-of-the-art phrase-based SMT systems use language model, phrase table or decoder to adjust the word order.
+Or an additional reordering model is used in the log-linear model for word reordering.
+However, these methods may have some disadvantages, such as some don't handle long-distance reordering, some don't handle unstructured reordering and some are rather time consuming.
+
+Encouraged by the results from the paper \cite{short}, \cite{long} and \cite{tree}, we further propose a new data-driven, rule-based preordering method, which extracts and applies reordering rules based on syntax tree.
+The method is called Multi-Level-Tree (MLT) reordering, which orders the constituents on multiple levels of the syntax tree all together.
+This preordering method rearranges the words in source language into a similar order as they are supposed to be in the target language before translation.
+With the appropriate word order, better translation quality can be achieved.
+Especially, our preordering method is very suitable for translation between language pairs like English and Chinese, which have very different word orders.
+Besides, the method can also be combined with the above mentioned rule-based reordering methods to achieve better translation quality.
+
+\section{Related Work}
+
+Word reordering is an important problem for statistical machine translation, which has long been addressed.
+
+In a phrase-based SMT system, there are several possibilities to change the word orders.
+Words can be reordered during the decoding phase by setting a window, which allows the decoder to choose the next word for translation.
+Reordering could also be influenced by the language model, because the language model give probability of how a certain word is likely to follow.
+Different language model may give different probability, which further influences the decision made by log-linear model.
+Other ways to change the word orders include using distance based reordering models or lexicalized reordering models \cite{tillmann2004, koehn2005}.
+The lexicalized reordering model reorders the phrases by using information of how the neighboring phrases change orientations.
+
+The hierarchical phrase-based translation model \cite{hier} is especially suitable for Chinese translation, and provide very good translation results.
+It extracts hierarchical rules by using information of the syntactic structure.
+Phrases from different hierarchies, or so-called phrases of phrases, are reordered during the decoding.
+
+The idea of phrases on different hierarchies has inspired us to create this preordering method based on multiple levels of the syntax tree.
+Besides, we also hope to detach the reordering from decoding phase and do it separately in a pre-process before decoding, in order to reduce the time for translation.
+This kind of preordering approaches use linguistic information to modify the word orders.
+
+Reordering approaches can also be rule-based, which extracts different types of reordering rules by observing reordering patterns from the training data and apply the rules to the sentences to be translated.
+Depends on how the rules are defined, different information may be used such as word alignments, POS tags, syntax trees, etc.
+
+Some early approaches use manually defined reordering rules based on the linguistic information for particular languages \cite{collins2005clause, popovic2006pos,habash2007syntactic}.
+Especially \cite{syntactic} is based on Chinese and has analyzed the reordering cases between English and Chinese based on syntactic structure.
+Later come the data-driven methods \cite{zhang2007chunk, crego2008using}, which learn the reordering rules automatically.
+
+\cite{short} introduced the idea of extracting reordering rules from the POS tag sequences of training data and use them for reordering.
+\cite{long} went further, and developed a method for long-distance word reordering, which works good on German-English translation task due to the long-distance shift of verbs.
+The method extracts discontinuous reordering rules in addition to the continuous ones, which contains a placeholder to match several words and enables the word to shift cross long distance.
+
+Afterwards, \cite{tree} introduced a novel approach to reorder the words based on syntax tree, which leads to further improvements on translation quality.
+The algorithm takes syntactic structure of the sentences into account and extract the rules from the syntax tree by detecting the reordering of child sequences.
+It also has the variant based only on part of the child sequences which is suitable for language with flat syntactic structure such as German.
+
+Recently, \cite{google} introduced a novel classified preordering approach.
+Unlike existing preordering models, it trains feature-rich discriminative classifiers that directly predict the target side word order.
+It reorders the children in subtrees in a similar manner as the syntax tree based method, but trains different classifiers for nodes with different number of children.
+
+However, these approaches which are bases on POS tag sequences or syntax trees are mostly designed for German and are not especially adapted for Chinese translation.
+As Chinese has very different word orders, a reordering approach, which can further explore the syntactic structure of Chinese and utilize this information for reordering, is desirable.
+
+Oracle reordering has also shown values for evaluating the potential of preordering.
+\cite{metrics} introduced the permutation distance metrics which can be used to measure reordering quality.
+And \cite{birch2} described how we can construct permutations from the word alignment as oracle reordering.
+
+\section{Motivation}
+
+\section{Multi-Level-Tree Reordering}
+
+\section{Results}
+
+\section{Conclusion}
 
@@
 References should be numbered in order of appearance, 
-for example \cite{ES1}, \cite{ES2}, and \cite{ES3}.
+for example %\cite{ES1}, \cite{ES2}, and \cite{ES3}.
 
@@
 
-%
-\bibliographystyle{IEEEtran}
-\begin{thebibliography}{10}
-\bibitem[1]{ES1} Smith, J. O. and Abel, J. S., 
-``Bark and {ERB} Bilinear Transforms'', 
-IEEE Trans. Speech and Audio Proc., 7(6):697--708, 1999.  
-\bibitem[2]{ES2} Lee, K.-F., Automatic Speech Recognition: 
-The Development of the 
-SPHINX SYSTEM, Kluwer Academic Publishers, Boston, 1989.
-\bibitem[3]{ES3} Rudnicky, A. I., Polifroni, Thayer, E. H.,
- and Brennan, R. A.  
-"Interactive problem solving with speech", J. Acoust. Soc. Amer., 
-Vol. 84, 1988, p S213(A).
-\end{thebibliography}
+\bibliographystyle{myieeetr}
+\bibliography{paper}
 \end{document}

### 2014-09-22 Paper/paper.tex
.

@@
 \usepackage{iwslt14,amssymb,amsmath,epsfig}
+\usepackage{tikz}
+\usetikzlibrary{arrows}
+\usetikzlibrary{trees}
+\usetikzlibrary{shapes}
+\usetikzlibrary{chains}
+\usetikzlibrary{calc}
+\usetikzlibrary{positioning}
+\usepackage[encapsulated]{CJK}
+\newcommand{\cntext}[1]{\begin{CJK}{UTF8}{gbsn}#1\end{CJK}}
 \setcounter{page}{1}
@@
 
+Another way to achieve word reordering is to detach it from decoding phase and do it separately in a pre-process before decoding, in order to reduce the time for translation.
+This kind of preordering approaches use linguistic information to modify the word orders.
+Preordering can also be rule-based, which extracts different types of reordering rules by observing reordering patterns from the training data and apply the rules to the sentences to be translated.
+Depends on how the rules are defined, different information may be used such as word alignments, POS tags, syntax trees, etc.
+
+Some early approaches use manually defined reordering rules based on the linguistic information for particular languages \cite{collins2005clause, popovic2006pos,habash2007syntactic,syntactic}.
+Later come the data-driven methods \cite{zhang2007chunk, crego2008using}, which learn the reordering rules automatically.
+
+Rottman and Vogel 2007 \cite{short} introduced the idea of extracting reordering rules from the POS tag sequences of training data and use them for reordering.
+Niehues and Kolss 2009 \cite{long} went further, and developed a method for long-distance word reordering, which works good on German-English translation task due to the long-distance shift of verbs.
+The method extracts discontinuous reordering rules in addition to the continuous ones, which contains a placeholder to match several words and enables the word to shift cross long distance.
+
+Afterwards, Herrmann et al.
+2013 \cite{tree} introduced a new approach to reorder the words based on syntax tree, which leads to further improvements on translation quality.
+The algorithm takes syntactic structure of the sentences into account and extract the rules from the syntax tree by detecting the reordering of child sequences.
+It also has the variant based only on part of the child sequences which is suitable for language with flat syntactic structure such as German.
+
+However, these approaches which are bases on POS tag sequences or syntax trees are mostly designed for languages like German and are not especially adapted for languages like Chinese.
+As Chinese has very different word orders, a reordering approach, which can further explore the syntactic structure of Chinese and utilize this information for reordering, is desirable.
+
 The hierarchical phrase-based translation model \cite{hier} is especially suitable for Chinese translation, and provide very good translation results.
@@
 
-Reordering approaches can also be rule-based, which extracts different types of reordering rules by observing reordering patterns from the training data and apply the rules to the sentences to be translated.
-Depends on how the rules are defined, different information may be used such as word alignments, POS tags, syntax trees, etc.
-
-Some early approaches use manually defined reordering rules based on the linguistic information for particular languages \cite{collins2005clause, popovic2006pos,habash2007syntactic}.
-Especially \cite{syntactic} is based on Chinese and has analyzed the reordering cases between English and Chinese based on syntactic structure.
-Later come the data-driven methods \cite{zhang2007chunk, crego2008using}, which learn the reordering rules automatically.
-
-\cite{short} introduced the idea of extracting reordering rules from the POS tag sequences of training data and use them for reordering.
-\cite{long} went further, and developed a method for long-distance word reordering, which works good on German-English translation task due to the long-distance shift of verbs.
-The method extracts discontinuous reordering rules in addition to the continuous ones, which contains a placeholder to match several words and enables the word to shift cross long distance.
-
-Afterwards, \cite{tree} introduced a novel approach to reorder the words based on syntax tree, which leads to further improvements on translation quality.
-The algorithm takes syntactic structure of the sentences into account and extract the rules from the syntax tree by detecting the reordering of child sequences.
-It also has the variant based only on part of the child sequences which is suitable for language with flat syntactic structure such as German.
-
-Recently, \cite{google} introduced a novel classified preordering approach.
-Unlike existing preordering models, it trains feature-rich discriminative classifiers that directly predict the target side word order.
-It reorders the children in subtrees in a similar manner as the syntax tree based method, but trains different classifiers for nodes with different number of children.
-
-However, these approaches which are bases on POS tag sequences or syntax trees are mostly designed for German and are not especially adapted for Chinese translation.
-As Chinese has very different word orders, a reordering approach, which can further explore the syntactic structure of Chinese and utilize this information for reordering, is desirable.
-
 Oracle reordering has also shown values for evaluating the potential of preordering.
@@
 
+The word order between English and Chinese differs very significantly.
+For one, the words in Chinese have generally different origins as those in English, which leads to very different vocabulary and word construction.
+Sometimes it is very hard to find corresponding words in the other language.
+For example, some prepositions in Chinese have very different usage than those prepositions in English.
+Also the continuous writing of Chinese without spaces makes this problem more severe, since word boundaries are not always so clear in Chinese.
+The text needs to be segmented first before translation.
+A word segmentation process is used to separate the words, but the results may not always be ideal.
+
+For the other, both languages have sometimes very different sentence structures.
+Thus, a word-for-word translation between English and Chinese is often unnatural or difficult to understand.
+Each of them has some sentence patterns that don't exist or rarely used in the other.
+In Chinese, a modifier is often put before the part that it modifies.
+While in English, it is very common that the modifier is put after the part that it modifies.
+Besides, English sentences with a lot of long clauses may be more suitable to translate into several Chinese sentences, because in Chinese people don't tend to use long clauses in general.
+
+Some typical problems of word orders between English and Chinese that we've found in the data are as follows:
+
+\begin{itemize}
+\item \emph{Pre-modifier instead of post-modifier.} In Chinese people tend to use pre-modifier rather than post-modifier.
+This involves the position change of adverbials, relative clauses and preposition phrases during translation.
+\item \emph{Constuction of questions.}
+\item \emph{Special sentence constructions.} For example, \emph{B\^{a}}-construction in Chinese and sentence constructions such as \emph{there be} and inverted negative sentences in English don't have correspondence in the other language in general.
+\item \emph{Long distance word position change.}
+\end{itemize}
+
+Not all these reordering problem can be solved well by using reordering rules based on POS tag sequence or single level of syntax tree.
+In order to improve the reordering between English and Chinese, we need reordering method that can handle more complicated, unstructural word order change.
+Inspired by the ideas of reordering on syntax tree and hierarchical phrases, we created the MLT reordering, which reorders words based on multiple syntactic levels and can handle long distance word position change and complicated word position change very well.
+
 \section{Multi-Level-Tree Reordering}
+\subsection{Reordering on Multiple Syntactic Levels}
+
+Reordering patterns are based on multiple levels of the syntax tree. Figure~\ref{unstructured}
+
+\begin{figure}
+\centering
+\scalebox{1}{\input{unstructured.tikz}}
+\caption{Reordering pattern from multiple syntactic levels}
+\label{unstructured}
+\end{figure}
+
+\subsection{Rule Extraction}
+\subsection{Rule Application}
 

### 2014-09-23 Paper/paper.tex
.

@@
 \documentclass[a4paper]{article}
-\usepackage{iwslt14,amssymb,amsmath,epsfig}
+\usepackage{iwslt14,amssymb,amsmath,epsfig,multirow,spreadtab,array}
 \usepackage{tikz}
@@
 \usetikzlibrary{positioning}
+\usepackage[T1]{fontenc}
+\usepackage[latin1,utf8x]{inputenc}
 \usepackage[encapsulated]{CJK}
@@
 Our results show that the approach has led to improved translation quality both when it was applied separately on the baseline or when it was combined with some other reordering approaches.
-We report an improvement of $0.43$ in BLEU score when our preordering approach was used in addition to the short rule \cite{short}, long rule\cite{long} and tree rule \cite{tree} based preordering approaches in the English-to-Chinese translation direction.
-There's also an improvement of $0.3$ in BLEU score when our preordering approach was used in addition to the aforementioned preordering approaches in the Chinese-to-English translation direction.
-Through the translation examples, we've also found improvements in syntactic structure with our preordering approach.
+As our reordering approach was used alone, it showed an improvement of $1.61$ in BLEU score in the English-to-Chinese translation direction and an improvement of $2.16$ in BLEU score in the Chinese-to-English translation direction, in comparison with the baseline, which used no preordering at all.
+As our preordering approach were combined with the short rule \cite{short}, long rule \cite{long} and tree rule \cite{tree} based preordering approaches, it showed an improvement of $0.43$ in BLEU score in the English-to-Chinese translation direction and an improvment of $0.3$ in BLEU score in the Chinese-to-English translation direction.
+Through the translations that used our preordering approach, we've also found improvements in syntactic structure.
 \end{abstract}
@@
 \begin{itemize}
-\item \emph{Pre-modifier instead of post-modifier.} In Chinese people tend to use pre-modifier rather than post-modifier.
+\item \emph{Pre-modifier instead of post-modifier}\\ In Chinese people tend to use pre-modifier rather than post-modifier.
 This involves the position change of adverbials, relative clauses and preposition phrases during translation.
-\item \emph{Constuction of questions.}
-\item \emph{Special sentence constructions.} For example, \emph{B\^{a}}-construction in Chinese and sentence constructions such as \emph{there be} and inverted negative sentences in English don't have correspondence in the other language in general.
-\item \emph{Long distance word position change.}
+\item \emph{Construction of questions}
+\item \emph{Special sentence constructions}\\ For example, \emph{B\^{a}}-construction in Chinese and sentence constructions such as \emph{there be} and inverted negative sentences in English don't have correspondence in the other language in general.
+\item \emph{Long distance word position change}
 \end{itemize}
 
-Not all these reordering problem can be solved well by using reordering rules based on POS tag sequence or single level of syntax tree.
+From previous work of others, the following types of reordering rules have been researched:
+
+\begin{itemize}
+\item \emph{Short rules} \cite{short} \\
+Short rules are extracted based on the sequences of adjacent words or their POS tags in the sentence from training data.
+Sequences of adjacent words or POS tags are observed, rules are then extracted if the same reordering patterns appear frequently.
+Following is a reordering pattern of a short rule:\medskip\\
+\texttt{WRB MD DT -> DT WRB MD}
+\item \emph{Long rules} \cite{long}\\
+Long rules are specially designed to improve the long distance word reordering for language pairs like English and German.
+The rules are based on POS tags of the text, and use a placeholder ($*$) to represent one or more words.
+Following is a reordering pattern of a long rule:\medskip\\
+\texttt{NN $*$ MD -> $*$ MD NN}
+
+\item \emph{Tree rules} \cite{tree}\\
+While short rules and long rules are based on the flat structure of sentences, tree rules reorder sentences by using information from sentences' syntactic structure.
+The syntax tree and word alignment of the training corpus are used to train the reordering rules.
+The tree rules reorder the words both on the word level and on the constituent level.
+Following is a reordering pattern of a tree rule:\medskip\\
+\texttt{NP ( ADJP JJ NN ) -> JJ NN ADJP}\medskip\\
+The parenthesis in the example represents the hierarchy in the syntax tree.
+The left side of the rule corresponds a tree with the root labeled with \emph{NP} and three children, each labeled with \emph{ADJP}, \emph{JJ} and \emph{NN}.
+\end{itemize}
+
+However, not all these reordering problem of Chinese translation can be solved well by using these reordering rules based either on POS tag sequence or single level of syntax tree.
 In order to improve the reordering between English and Chinese, we need reordering method that can handle more complicated, unstructural word order change.
@@
 
-Reordering patterns are based on multiple levels of the syntax tree. Figure~\ref{unstructured}
+Reordering patterns are based on multiple levels of the syntax tree.
+Figure~\ref{unstructured} illustrates how the reordering patterns are detected from the syntax tree.
+In the example, the detection starts from the root node, go downwards three levels and use the nodes in these levels to detect the reordering pattern.
+These nodes that are used for detecting the reordering pattern are colored gray and have an italic font.
+The leaf nodes in the syntax tree indicate words in the sentence, which has rectangle shape with angular corners.
+
+According to the alignment information with the corresponding Chinese translation, the node labeled with \emph{NP} is moved forward to the first place in the translation and the node labeled with \emph{IN of} is moved forward to the second place in translation.
+So from the root node with a search depth $3$, the following reordering pattern can be found:\bigskip
+
+\noindent \texttt{NP ( \textbf{CD}$_0$ NP ( NP ( \textbf{JJ}$_1$ \textbf{NNS}$_2$ ) PP ( \textbf{IN}$_3$ \textbf{NP}$_4$ ) ) ) -> NP IN CD JJ NNS}\medskip \\
+\texttt{or -> 4 3 0 1 2 (with index)}\bigskip
+
+where the POS tags in bold corresponds to words in the leaf nodes of the syntax tree, which are parts that are actually reordered and have a darker gray color in the figure.
+The parentheses in the reordering pattern indicate the corresponding hierarchies in the syntax tree.
+The reordering can be alternatively represented with index, which is the actual internal representation to avoid ambiguity caused by POS tags with the same name and we use this representation throughout this paper.
 
@@
 \centering
-\scalebox{1}{\input{unstructured.tikz}}
-\caption{Reordering pattern from multiple syntactic levels}
+\scalebox{1.3}{\input{unstructured.tikz}}
+\caption{Detection of reordering pattern from multiple syntactic levels}
 \label{unstructured}
@@
 \subsection{Rule Extraction}
+
+In order to find as much information for reordering as possible.
+The algorithm of rule extraction detects the reordering patterns from all nodes in the syntax tree and it goes downwards for any number of hierarchies, until it reaches the lowest hierarchy in the subtrees.
+
+In the implementation, the program conducts a depth-first search (DFS) to traverse every node in a syntax tree.
+Every time when a node is reached, the program conducts another iterative deepening depth-first search (IDDFS) in its subtree with depth-limit from $1$ to the subtree's depth.
+And the program detects if there are any patterns of word position changes at the same time, by using the alignment for comparison.
+
+The detected word position changes are checked for their validity for reordering rules.
+A valid reordering pattern should both has actual word reordering and clearly distinguishable new order on the side of the target language, i.e.
+no collision of aligned ranges on the target side.
+
+\begin{figure}
+\centering
+\scalebox{1.3}{\input{extract.tikz}}
+\caption{A phrase with its syntax tree and alignment for rule extraction}
+\label{extract}
+\end{figure}
+
+Figure~\ref{extract} shows a phrase to be translated, together with its syntax tree and word alignment of parallel text.
+The leaf nodes are underlined and indexed according to the order they appear in the left side of the patterns.
+The index sequences on the right side of the patterns indicate the reordering.
+In this example, we can find the following reordering patterns:\bigskip
+
+\noindent From node $1$:\\
+\texttt{NP ( \textbf{NP} \textbf{PP} ) -> 1 0} \hfill [1 level]\hphantom{s}\\
+\texttt{NP ( NP ( \textbf{JJ} \textbf{NNS} ) PP ( \textbf{IN} \textbf{NP} ) ) -> 3 2 0 1} \hfill [2 levels]\\
+\texttt{NP ( NP ( \textbf{JJ} \textbf{NNS} ) PP ( \textbf{IN} NP ( \textbf{JJ} \textbf{NNS} ) ) ) -> 3 4 2 0 1} \hfill [3 levels]\medskip
+
+\noindent From node $3$:\\
+\texttt{PP ( \textbf{IN} \textbf{NP} ) -> 1 0} \hfill [1 level]\hphantom{s}\\
+\texttt{PP ( \textbf{IN} NP ( \textbf{JJ} \textbf{NNS} ) ) -> 1 2 0} \hfill [2 levels]\bigskip
+
+The probability of the reordering patterns are calculated based on frequency of their occurrences in the training corpus.
+There are the left part and the right part of the reordering patterns separated by the arrow.
+The left part indicates the syntactic tags that should be reordered and the right part indicates how the new order should be like.
+The probability of the pattern is calculated by how often the left part is reordered into the right part among all its appearances in the training corpus.
+In addition, reordering patterns that appear less than a threshold are ignored to be used as reordering rules, in order to prevent too concrete rules without generalization capability and overfitting.
+
 \subsection{Rule Application}
 
-\section{Results}
+The syntax tree is traversed by DFS as the same in rule extraction.
+But from the root of each subtree, it's scanned with depth limit from its maximal levels, i.e.
+its depth, to $1$.
+As it turns out, any rule can be applied for a subtree at some level, a new path for this reordering will be added to the word lattice for decoding.
+As long as rules can be applied on a subtree for a certain depth, the rules are applied and the search for rule application on this subtree stops, and the search on the next subtree continues.
 
-\section{Conclusion}
+The reason for this is to prevent duplicate reorderings due to application of nested rules, which has overlapped effect with each other.
+These rules are normally patterns that are generated on the same subtree, but with different number of levels, which has different generalization effect on the same range of words in the text.
+For example, the following patterns can be detected from the syntax tree in figure~\ref{extract}:\bigskip
 
-\subsection{First page}
+\noindent \texttt{PP ( \textbf{IN} \textbf{NP} ) -> 1 0}\\
+\texttt{PP ( \textbf{IN} NP ( \textbf{JJ} \textbf{NNS} ) ) -> 1 2 0}\bigskip
 
-The first page should have the paper title, author(s), and affiliation(s)
-centered on the page across both columns. The remainder of the text 
-must be in the two-column format, staying within the indicated image 
-area.
+Both patterns are detected from the same node, but the second pattern is detected by retrieving the nodes one level deeper and it's more concrete.
+So the first pattern can be seen as a generalization of the second pattern.
+Whenever a rule of the second pattern can be applied, a rule of the first pattern can be applied too.
+Because subtrees are checked from the highest number of levels in rule application, the more concrete rule is applied first.
+Because the more concrete rule fits the detected pattern better and contains more details of reordering, so it may be more suitable for rule application.
+In this example, the second rule is applied rather than the first rule.
 
-\subsubsection{Paper Title}
-The paper title must be in boldface. All non-function words must be capitalized,
-and all other words in the title must be lower case. The paper title is centered
-across the top of the two columns on the first page as indicated above.
+Word reorderings are added to the word lattice as paths, which is further past to the decoder for translation.
+Paths with very low probability are removed, in order to save space for storing the lattice and reduce decoding time later, without compromising too much translation quality.
 
-\subsubsection{Authors' Name(s)}
-The authors' name(s) and affiliation(s) appear centered below the paper
-title. If space permits, include a mailing address here. The templates indicate
-the area where the title and author information should go. These items need not
-be confined to the number of lines indicated; papers with multiple
-authors and affiliations may require two or more lines. 
-Note that the submission version of technical papers \emph{should be 
-anonymized for review}.
+\subsection{Rule Combination}
 
-\subsubsection{Abstract}
-Each paper must contain an abstract that appears at the beginning of the paper.
+In order to further explore the probability of improvement, the MLT reordering rules can be combined with other types of reordering rules to achieve further improvements.
+This is done by training the different types of rules separately and applying them on the monotone path of the sentence independently.
+They generate different paths in the word lattice.
 
-\subsection{Basic layout features}
+\section{Experiments}
 
-\begin{itemize}
-%\itemsep -1.3mm
-\item Proceedings will be printed in A4 format. The layout is designed 
-so that files, when printed in US Letter format, include all material 
-but margins are not symmetric. 
-Although this is not an absolute requirement, if at all possible,
-{\bf PLEASE TRY TO MAKE YOUR SUBMISSION IN A4 FORMAT.}
-\item Two columns are used except for the title part and possibly for large 
-figures that need a full page width.
-\item Left margin is 20 mm.
-\item Column width is 80 mm.
-\item Spacing between columns is 10 mm.
-\item Top margin 25 mm (except first page 30 mm to title top).
-\item Text height (without headers and footers) is maximum 235 mm.
-\item Headers and footers must be left empty (they will be added for 
-printing).
-\item Check indentations and spacings by comparing to this 
-example file (in pdf format).
-\end{itemize}
+We've conducted experiments on both English-to-Chinese and Chinese-to-English translation directions to get a better overview of the MLT reordering's effect.
+In the experiments, the MLT reordering rules are also combined with other reordering rules that are introduced before, in order to show the improvement achieved by our approach.
 
-\subsubsection{Headings}
+In order to evaluate the potential of word reordering, we also used oracle reordering in the experiments.
+Oracle reordering is considered to be an optimally reordered sentence as input to the SMT system and do not allow additional reordering during decoding.\cite{combine} The oracle reordering is created by using the permutation of source sentences, which is extracted from the word alignment between the source text and reference.\cite{birch2}
 
-Section headings are centered in boldface
-with the first word capitalized and the rest of the heading in 
-lower case. Sub-headings appear like major headings, except they 
-start at the left margin in the column.
-Sub-sub-headings appear like sub-headings, except they are in italics 
-and not boldface. See the examples given in this 
-file. No more than 3 levels of headings should be used.
+Because oracle reordering is considered as an optimally reordering, we can use it as input of the SMT system and the scores are the optimal results that can be achieved by word reordering, from which we can evaluate the potential of reordering methods.
 
-\subsection{Text font}
+\subsection{English-to-Chinese System}
 
-Times or Times Roman font is used for the main text. Recommended 
-font size is 9 points which is also the minimum allowed size.
-Other font types may be used if needed for 
-special purposes. While making the final PostScript file, 
-remember to include all fonts!
+We performed experiments with or without different reordering methods covering the English-to-Chinese translation direction.
+The reordering methods included our MLT reordering approach and the other reordering approaches with short rules, long rules and tree rules.
+The system was trained on news text from the LDC corpus and subtitles from TED talks.
+The development data and test data were both news text from the LDC corpus.
+The system was a phrase-based SMT system, which used a $6$-gram language model with Knersey-Ney smoothing.
+Besides the preordering, no lexical reordering or other reordering method in decoding phase was used.
+The text was translated through a monotone decoder.
 
-\LaTeX\ users: DO NOT USE Computer Modern FONT FOR TEXT (Times is 
-specified in the style file). If possible, make the final 
-document using POSTSCRIPT FONTS.
-This is necessary given that, for example, equations with 
-non-ps Computer Modern are very hard to read on screen.
+The reordering rules were extracted by using the word alignments, POS tags and syntax trees from the training data.
+One reference of the test data was used for evaluating the results.
+The threshold for rule extraction is set as $5$ times and reordering paths with probability less than $0.1$ are not added to word lattices.
+The decoder was a monotone decoder.
+Table~\ref{denw} shows the size of data used in the system.
 
-\subsection{Figures}
+\begin{table*}
+\centering
+\begin{tabular}{|ll|r|r|r|r|r|}
+\hline
+\multicolumn{2}{|l|}{\multirow{2}{*}{Data Set}} & \multirow{2}{*}{Sentence Count} & \multicolumn{2}{c|}{Word Count} & \multicolumn{2}{c|}{Size (Byte)}\\ \cline{4-7}
+& & & English & Chinese & English & Chinese \\
+\hline
+\multirow{2}{*}{Training Data} & \multicolumn{1}{|l|}{LDC} & 303K & 10.96M & 8.56M & 60.88M & 47.27M \\ \cline{2-7}
+& \multicolumn{1}{|l|}{TED} & 151K & 2.58M & 2.86M & 14.24M & 15.63K \\ \hline
+\multicolumn{2}{|l|}{Development Data} & 919 & 30K & 25K & 164K & 142K \\ \hline
+\multicolumn{2}{|l|}{Test Data} & 1663 & 47K & 38K & 263K & 220K \\ \hline
+\end{tabular}
+\caption{Data details in English-to-Chinese system}
+\label{denw}
+\end{table*}
 
-All figures must be centered on the column (or page, if the figure spans 
-both columns).
-Figure captions should follow each figure and have the format given in 
-Fig.~\ref{spprod}.
-
-Figures should preferably be line drawings. If they contain gray 
-levels or colors, they should be checked to print well on a 
-high-quality non-color laser printer.
-
-\subsection{Tables}
-
-An example of a table is shown as Table \ref{table1}. Somewhat 
-different styles are allowed according to the type and purpose of the 
-table. The caption text may be above or below the table.
-
-\begin{table} [t,h]
-\caption{\label{table1} {\it This is an example of a table.}}
-\vspace{2mm}
-\centerline{
-\begin{tabular}{|c|c|}
+\begin{table}
+\centering
+\STautoround*{2}
+\begin{spreadtab}{{tabular}{|l|r|r|r|}}\hline
+@				& @BLEU (\%) & @ Imprv. & @TER (\%) \\ \hline
+@Baseline		& 12.07 & & 72.15 \\ \hline
+@+Short Rules	& 12.50 & :={b3 - b2} & 71.41 \\ \hline
+@+Long Rules   & 12.99 & :={b4 - b2} & 70.71 \\ \hline
+@+Tree Rules   & 13.38 & :={b5 - b2} & 68.27 \\ \hline
+\textbf{@+MLT Rules} & \textbf{:={13.81}} & \textbf{:={b6 - b2}} & \hphantom{xxx}\textbf{:={68.20}} \\ \hline
+@Oracle Reordering & :={18.58} & :={b7 - b2} & :={62.13} \\ \hline
 \hline
-ratio & decibels \\
-\hline  \hline
-1/1 & 0 \\
-2/1 & $\approx 6$ \\
-3.16 & 10 \\
-10/1 & 20 \\ 
-1/10 & -20 \\
-\hline
-\end{tabular}}
+@Long Rules   & 12.31 & :={b8 - b2} & 71.81\\ \hline
+@Tree Rules   & 13.30 & :={b9 - b2} & 70.42 \\ \hline
+\textbf{@MLT Rules}    & \textbf{:={13.68}} & \textbf{:={b10 - b2}} & \textbf{:={70.25}} \\ \hline
+\end{spreadtab}
+\caption{Result overview of English-to-Chinese system}
+\label{tenw}
 \end{table}
 
-\subsection{Equations}
+Table~\ref{tenw} shows the BLUE scores, absolute improvements of BLEU scores and TER scores for configurations with different reordering methods.
+The table consist of $2$ sections.
+the first row of the top section shows results of the baseline, which used no preordering at all.
+In the following rows of the top section, different types of reordering rules are combined gradually, with each type per row, and the results are showed.
+For example, the row with \emph{$+$MLT} Rules presents the configuration with all the rule types including MLT rules and all the other rules in the rows above.
+All improvements are absolute improvements of BLEU scores in comparison to the baseline.
+Each row with a certain reordering type presents all the different variations of this type and the best score under these configurations are shown.
+For example, long rules include the left rules and right rules, and the tree rules include the partial rules and recursive application.
+The baseline used a monotone decoder and no preordering.
+The row with \emph{oracle reordering} shows the results from the configuration that used the oracle reordering as input.
+The results of oracle reordering can be used for analyzing the potential of source sentence reordering.
+In the lower section of the table, different rule types are not combined and the effect of each rule type is shown.
 
-Equations should be placed on separate lines and numbered. Examples 
-of equations are given below.
-Particularly,
-%
-%\vspace{-3mm}
-\begin{equation}
-x(t) = s(f_\omega(t))
-\label{eq1}
-\end{equation}
-where \(f_\omega(t)\) is a special warping function
-\begin{equation}
-f_\omega(t)=\frac{1}{2\pi j}\oint_C \frac{\nu^{-1k}d\nu}
-{(1-\beta\nu^{-1})(\nu^{-1}-\beta)}
-\label{eq2}
-\end{equation}
-A residue theorem states that
-\begin{equation}
-\oint_C F(z)dz=2 \pi j \sum_k Res[F(z),p_k]
-\label{eq3}
-\end{equation}
-Applying (\ref{eq3}) to (\ref{eq1}), 
-it is straightforward to see that
-\begin{equation}
-1 + 1 = \pi
-\label{eq4}
-\end{equation}
+\subsection{Chinese-to-English System}
 
-Make sure to use \verb!\eqref! when refering to equation numbers.
-Finally we have proven the secret theorem of all speech sciences (see
-equation~\eqref{eq3} above).  No more math is needed to show how 
-useful the result is!
+The experiments for Chinese-to-English systems had a similar setup as described in the last section.
+The parallel data used in the English-to-Chinese system was also used in this experiment by switching the source language and the target language.
+We only used the LDC data set for training, and no TED data were used in this system.
+The test data had three English references for evaluating the results instead of one as in the previous system.
+The data used are summarized in table~\ref{dzhen2}.
 
-\begin{figure}[t]
-\centerline{\epsfig{figure=figure,width=40mm}}
-\caption{{\it Schematic diagram of speech production.}}  
-\label{spprod}
-\end{figure}
+\begin{table*}
+\centering
+\begin{tabular}{|l|r|r|r|r|r|}
+\hline
+\multirow{2}{*}{Data Set} & \multirow{2}{*}{Sentence Count} & \multicolumn{2}{c|}{Word Count} & \multicolumn{2}{c|}{Size (Byte)}\\ \cline{3-6}
+& & Chinese & English & Chinese & English \\
+\hline
+Training Data & 303K & 8.56M & 10.96M & 47.27M & 60.88M\\ \hline
+Development Data & 919 & 25K & 30K & 142K & 164K \\ \hline
+Test Data & 1663 & 38K & 47K & 220K & 263K \\ \hline
+\end{tabular}
+\caption{Data details in Chinese-to-English system}
+\label{dzhen2}
+\end{table*}
 
-\subsection{Hyperlinks}
+\begin{table}
+\centering
+\STautoround*{2}
+\begin{spreadtab}{{tabular}{|l|r|r|r|}}\hline
+@				& @BLEU (\%) & @Imprv. & @TER (\%) \\ \hline
+@Baseline		& 21.80 & & 62.09 \\ \hline
+@+Short Rules	& 22.90 & :={b3 - b2}& 61.64 \\ \hline
+@+Long Rules   & 23.13 & :={b4 - b2} & 61.43\\ \hline
+@+Tree Rules   & 23.84 & :={b5 - b2} & 60.95\\ \hline
+\textbf{@+MLT Rules}    & \textbf{:={24.14}} & \textbf{:={b6 - b2}} & \hphantom{xxx} \textbf{:={60.79}}\\ \hline
+@Oracle Reordering & :={26.80} & :={b7 -b2} & :={56.97} \\ \hline
+\hline
+@Long Rules   & 22.10 & :={b8 - b2} & 62.21\\ \hline
+@Tree Rules   & 23.35 & :={b9 - b2} & 61.52\\ \hline
+\textbf{@MLT Rules}    & \textbf{:={23.96}} & \textbf{:={b10 - b2}} & \textbf{:={60.83}}\\ \hline
+\end{spreadtab}
+\caption{Result overview of Chinese to English systems}
+\label{tzhen2}
+\end{table}
 
-Hyperlinks can be included in your paper. Moreover, be aware that the paper
-submission procedure includes the option of specifying a hyperlink for
-additional information.  This hyperlink will be included in the CD-ROM.
-Particularly pay attention to the possibility, from this single hyperlink, to
-have further links to information such as other related documents, sound or
-multimedia.
+Table~\ref{tzhen2} shows the results for configurations with different reordering methods for the Chinese-to-English translation.
+The table can be interpreted in the same manner as table~\ref{tenw} in the previous section.
 
-If you choose to use active hyperlinks in your paper, 
-please make sure that they present no problems in printing to paper.
+\subsection{Evaluation}
 
-\subsection{Page numbering}
+The results shows increasing scores as we used reordering methods from short rules, long rules, tree rules to MLT rules.
+And better BLEU scores were achieved as we combined the different reordering rules.
+The MLT rules achieved better BLEU scores and TERs in both translation directions, not only when it was used alone, but also it was added to the other reordering rules.
+As the MLT reordering rules were used alone, it showed an improvement of $1.61$ in BLEU score in the English-to-Chinese translation direction and an improvement of $2.16$ in BLEU score in the Chinese-to-English translation direction, in comparison with the baseline, which used no reordering at all.
+As the MLT reordering rules were combined with the other existing reordering rules, a further improvement of $0.43$ in BLEU score (from $13.38$ to $13.81$) was shown in the English-to-Chinese translation direction, as well as a further improvement of $0.3$ in BLEU score (from $23.84$ to $24.14$) in the Chinese-to-English translation direction.
 
-Final page numbers will be added later to the document
-electronically. 
-{\em Please don't make any headers or footers!}.
+We've also found improvements in the sentence structure.
+Table~\ref{te} shows some translation examples in both translation directions.
+Sections are separated by double lines in the table.
+Each section of this table shows one translation example with the source sentence (\emph{source}), translation without using MLT reordering (\emph{no MLT}), translation with MLT reordering (\emph{MLT}) and the reference (\emph{reference}).
+The translation without using MLT reordering comes from the configuration with highest BLEU score that didn't use MLT reordering.
+And the translation with MLT reordering comes from the configuration with highest BLEU score that used MLT reordering.
+From the examples, we can clearly see the improvements in sentence structure.
 
-\subsection{References}
+\begin{table*}
+\centering
+\begin{tabular}{|l|m{0.7\textwidth}|} \hline
+Source & hu jintao also extended deep condolences on the death of the chinese victims and expressed sincere sympathy to the bereaved families .
+\\ \hline
+No MLT & \cntext{胡锦涛 还 表示 深切 哀悼 的 受害者 家属 的 死亡 , 向 迂难者 家属 表示 诚挚 的 慰问 。} \\ \hline
+MLT & \cntext{胡锦涛 还 对 中国 迂难者 表示 哀悼 , 向 迂难者 家属 表示 诚挚 的 慰问 。} \\ \hline 
+Reference & \cntext{胡锦涛 还 对 中方 不幸 遇难 人员 表示 深切 的 哀悼 , 并 向 遇难 着 的 亲属 致以 诚挚 的 慰问 。} \\ \hline \hline
+Source & satisfying personal interests and expanding knowledge are also major reasons why hourly work appeals to people .\\ \hline
+No MLT & \cntext{满足 个人 利益 和 扩大 知识 也 是 主要 原因 小时 工作 吸引 人 。} \\ \hline
+MLT & \cntext{满足 个人 利益 和 扩大 知识 也 是 为什么 学生 工作 吸引 人 的 主要 原因 。} \\ \hline 
+Reference & \cntext{满足 个人 兴趣 , 扩大 自己 的 知识面 也 是 兼职 小时 工 受 青睐 的 一 个 重要 原因 。} \\ \hline \hline
 
-The reference format is the standard for IEEE publications.
-References should be numbered in order of appearance, 
-for example %\cite{ES1}, \cite{ES2}, and \cite{ES3}.
+Source & the dalai lama will go to visit washington this month .\\ \hline
+No MLT & \cntext{达赖 喇嘛 将 访问 华盛顿 的 这 一 个 月 。} \\ \hline
+MLT & \cntext{达赖 喇嘛 将 本 月 访问 华盛顿 。} \\ \hline
+%? add more examples?
+Reference & \cntext{达赖 喇嘛 将 在 本 月 前往 华盛顿 访问 。} \\ \hline \hline
+Source & \cntext{陈至立 说 , 古巴 是 拉美 和 加勒比 地区 有 重要 影响 的 国家 。}
+\\ \hline
+No MLT & chen zhili said : cuba is the latin america and the caribbean region has an important influence on the state .
+\\ \hline
+MLT & chen zhili said : cuba is a country of important influence latin america and the caribbean region .
+\\ \hline
+Reference & chen zhili said that cuba is a country of great influence in the latin american and caribbean region .
+\\ \hline \hline
 
-\section{Experiments}
-Please make sure to give all the necessary details regarding your experimental 
-setting so as to ensure that your results could be reproduced by other teams.
+Source & \cntext{近年 来 , 两 国 教育 交流 日益 密切 , 人员 来往 频繁 。}
+\\ \hline
+no MLT & in recent years , the two countries education have been increasingly close exchanges and personnel contacts have been frequent .
+\\ \hline
+MLT & in recent years , the educational exchanges between the two countries have become increasingly frequent , and have had frequent contacts .
+\\ \hline
+Reference & in recent years , the educational exchange between the two countries has become increasingly close with frequent personnel visits .
+\\ \hline
+
+\end{tabular}
+\caption{Examples of translations}
+\label{te}
+\end{table*}
+
+However, by taking a close look at the gap between the scores of oracle reordering and the best scores achieved by MLT reordering, we can also see, there's still potential for improvements of translation between English and Chinese through better reordering methods.
+
+From these experiments we can draw the conclusion that our reordering method obviously improves the sentence structure and  translation quality in both English-to-Chinese and Chinese-to-English translation directions, no matter when we apply it alone or when we combine it with short rules, long rules and tree rules.
 
@@
 
-This paper has described a novel approach for doing wonderful stuff such as ...
+We've present a new preordering approach for translation between English and Chinese.
+The algorithm detects and applies reordering rules uses information of word alignment and multiple syntactic levels in the syntax tree to reorder the source sentences.
+Reordering patterns are detected by checking if the nested tag sequences in subtrees with any number of search levels have clearly new orders in the aligned text in the target language.
 
-\section{Acknowledgements}
-The IWSLT 2014 organizing committee would like to thank the
-organizing committees of INTERSPEECH 2004 for their
-help and for kindly providing the template files.
+We've conducted experiments in both translation directions between English and Chinese with different SMT configurations.
+From the results we can see the BLEU scores was improved no matter when we applied the SMT reordering method to the baseline directly or when we combined it with the other reordering methods we introduced before, i.e.
+short rules, long rules and tree rules based reordering methods.
+
+When our approach was applied alone, it achieved an BLEU score improvement of $1.61$ in the English-to-Chinese translation direction, and an BLEU score improvement of $2.16$ in the Chinese-to-English translation direction.
+
+When our approach was combined with the short rules, long rules and tree rules based reordering methods, further improvements were achieved for both translation direction.
+Our approach improved the BLEU score further by $0.43$ in the English-to-Chinese translation direction and by $0.30$ in the Chinese-to-English translation direction.
+
+Besides the improvement in BLEU scores, our preordering approach also showed improvement in the sentence structure of the translation.
 

### 2014-09-24 Paper/paper.tex
.

@@
 \section{Multi-Level-Tree Reordering}
+
+Our preordering method is based on reordering rules.
+Reordering rules show how sentences should be reordered in source language before translation.
+In our system, the rules are generated by using the word alignment, and syntax tree, all of which are calculated based on the training data.
+After reordering rules are applied to the source sentences, word lattices are generated.
+A word lattice contains all the reordering possibilities of a source sentence and is further passed to the decoder for translation.
+The preordering system could be illustrated as figure~\ref{prereordering}.
+
+\begin{figure*}
+\centering
+\input{prereordering.tikz}
+\caption{Illustration of preordering system}
+\label{prereordering}
+\end{figure*}
+
 \subsection{Reordering on Multiple Syntactic Levels}
@@
 \centering
-\scalebox{1.3}{\input{unstructured.tikz}}
+\input{unstructured.tikz}
 \caption{Detection of reordering pattern from multiple syntactic levels}
@@
 \centering
-\scalebox{1.3}{\input{extract.tikz}}
+\input{extract.tikz}
 \caption{A phrase with its syntax tree and alignment for rule extraction}

### 2014-09-24 Paper/paper.tex
.

@@
 We propose a novel data-driven rule-based preordering approach, which uses the information of syntax tree and word alignment to reorder the words in source sentences before decoding in a phrase-based SMT system between English and Chinese.
-The preorering algorithm extracts reordering patterns from multiple levels of the syntax trees of the training data and applies the rules on the source sentences in a similar manner.
+The preordering algorithm extracts reordering patterns from multiple levels of the syntax trees of the training data and applies the rules on the source sentences in a similar manner.
 We've conducted experiments in English-to-Chinese and Chinese-to-English translation directions.
@@
 As our reordering approach was used alone, it showed an improvement of $1.61$ in BLEU score in the English-to-Chinese translation direction and an improvement of $2.16$ in BLEU score in the Chinese-to-English translation direction, in comparison with the baseline, which used no preordering at all.
-As our preordering approach were combined with the short rule \cite{short}, long rule \cite{long} and tree rule \cite{tree} based preordering approaches, it showed an improvement of $0.43$ in BLEU score in the English-to-Chinese translation direction and an improvment of $0.3$ in BLEU score in the Chinese-to-English translation direction.
+As our preordering approach were combined with the short rule \cite{short}, long rule \cite{long} and tree rule \cite{tree} based preordering approaches, it showed an improvement of $0.43$ in BLEU score in the English-to-Chinese translation direction and an improvement of $0.3$ in BLEU score in the Chinese-to-English translation direction.
 Through the translations that used our preordering approach, we've also found improvements in syntactic structure.
@@
 
-Rottman and Vogel 2007 \cite{short} introduced the idea of extracting reordering rules from the POS tag sequences of training data and use them for reordering.
+Rottmann and Vogel 2007 \cite{short} introduced the idea of extracting reordering rules from the POS tag sequences of training data and use them for reordering.
 Niehues and Kolss 2009 \cite{long} went further, and developed a method for long-distance word reordering, which works good on German-English translation task due to the long-distance shift of verbs.
@@
 \input{extract.tikz}
-\caption{A phrase with its syntax tree and alignment for rule extraction}
+\caption{A phrase with its syntax tree and word alignment for rule extraction}
 \label{extract}
@@
 
-Table~\ref{tenw} shows the BLUE scores, absolute improvements of BLEU scores and TER scores for configurations with different reordering methods.
+Table~\ref{tenw} shows the BLEU scores, absolute improvements of BLEU scores and TER scores for configurations with different reordering methods.
 The table consist of $2$ sections.
@@
 \end{spreadtab}
-\caption{Result overview of Chinese to English systems}
+\caption{Result overview of Chinese-to-English systems}
 \label{tzhen2}
@@
 And better BLEU scores were achieved as we combined the different reordering rules.
-The MLT rules achieved better BLEU scores and TERs in both translation directions, not only when it was used alone, but also it was added to the other reordering rules.
+The MLT rules achieved better BLEU scores and TER scores in both translation directions, not only when it was used alone, but also it was added to the other reordering rules.
 As the MLT reordering rules were used alone, it showed an improvement of $1.61$ in BLEU score in the English-to-Chinese translation direction and an improvement of $2.16$ in BLEU score in the Chinese-to-English translation direction, in comparison with the baseline, which used no reordering at all.

### 2014-09-24 Paper/paper.tex
.

@@
 \address{Institute for Anthropomatics \\
-Karlsruhe Institute of Technoloy, Germany \\
+Karlsruhe Institute of Technology, Germany \\
 {\small \tt utcur@student.kit.edu, yuqi.zhang@kit.edu}
@@
 We propose a novel data-driven rule-based preordering approach, which uses the information of syntax tree and word alignment to reorder the words in source sentences before decoding in a phrase-based SMT system between English and Chinese.
-The preordering algorithm extracts reordering patterns from multiple levels of the syntax trees of the training data and applies the rules on the source sentences in a similar manner.
+The preordering algorithm extracts reordering patterns from multiple levels of the syntax trees of the training data and applies the rules on the source sentences in a similar way.
 We've conducted experiments in English-to-Chinese and Chinese-to-English translation directions.
 Our results show that the approach has led to improved translation quality both when it was applied separately on the baseline or when it was combined with some other reordering approaches.
-As our reordering approach was used alone, it showed an improvement of $1.61$ in BLEU score in the English-to-Chinese translation direction and an improvement of $2.16$ in BLEU score in the Chinese-to-English translation direction, in comparison with the baseline, which used no preordering at all.
-As our preordering approach were combined with the short rule \cite{short}, long rule \cite{long} and tree rule \cite{tree} based preordering approaches, it showed an improvement of $0.43$ in BLEU score in the English-to-Chinese translation direction and an improvement of $0.3$ in BLEU score in the Chinese-to-English translation direction.
+As our reordering approach was used alone, it showed an improvement of $1.61$ in BLEU score in the English-to-Chinese translation direction and an improvement of $2.16$ in BLEU score in the Chinese-to-English translation direction, in comparison with the baseline, which used no word reordering.
+As our preordering approach were combined with the short rule \cite{short}, long rule \cite{long} and tree rule \cite{tree} based preordering approaches, it showed further improvements of up to $0.43$ in BLEU score in the English-to-Chinese translation direction and further improvements of up to $0.3$ in BLEU score in the Chinese-to-English translation direction.
 Through the translations that used our preordering approach, we've also found improvements in syntactic structure.
@@
 Or an additional reordering model is used in the log-linear model for word reordering.
-However, these methods may have some disadvantages, such as some don't handle long-distance reordering, some don't handle unstructured reordering and some are rather time consuming.
+However, these methods may have some disadvantages, such as some don't handle long-distance reordering, some don't handle unstructured reordering and some are rather time-consuming.
 
-Encouraged by the results from the paper \cite{short}, \cite{long} and \cite{tree}, we further propose a new data-driven, rule-based preordering method, which extracts and applies reordering rules based on syntax tree.
+Encouraged by the results from the result from Rottmann and Vogel 2007 \cite{short}, Niehues and Kolss 2009 \cite{long} and Herr\-mann et al.
+2013 \cite{tree}, we further propose a new data-driven, rule-based preordering method, which extracts and applies reordering rules based on syntax tree.
 The method is called Multi-Level-Tree (MLT) reordering, which orders the constituents on multiple levels of the syntax tree all together.
 This preordering method rearranges the words in source language into a similar order as they are supposed to be in the target language before translation.
-With the appropriate word order, better translation quality can be achieved.
+With the proper word order, better translation quality can be achieved.
 Especially, our preordering method is very suitable for translation between language pairs like English and Chinese, which have very different word orders.
@@
 Niehues and Kolss 2009 \cite{long} went further, and developed a method for long-distance word reordering, which works good on German-English translation task due to the long-distance shift of verbs.
-The method extracts discontinuous reordering rules in addition to the continuous ones, which contains a placeholder to match several words and enables the word to shift cross long distance.
+The method extracts discontinuous reordering rules in addition to the continuous ones, which uses a placeholder to match several words and enables the word to shift cross long distance.
 
@@
 
-The word order between English and Chinese differs very significantly.
+The word order between English and Chinese differs very much.
 For one, the words in Chinese have generally different origins as those in English, which leads to very different vocabulary and word construction.
@@
 This involves the position change of adverbials, relative clauses and preposition phrases during translation.
-\item \emph{Construction of questions}
+\item \emph{Construction of questions}\\
+The two languages have very different ways to construct questions, which raises word order problems for translating questions.
 \item \emph{Special sentence constructions}\\ For example, \emph{B\^{a}}-construction in Chinese and sentence constructions such as \emph{there be} and inverted negative sentences in English don't have correspondence in the other language in general.
-\item \emph{Long distance word position change}
+\item \emph{Long distance word position change}\\
+Word reordering between English and Chinese often involves word shift cross long distance.
 \end{itemize}
@@
 \item \emph{Short rules} \cite{short} \\
-Short rules are extracted based on the sequences of adjacent words or their POS tags in the sentence from training data.
+Short rules are extracted based on the sequences of adjacent words or their POS tags in sentences from training data.
 Sequences of adjacent words or POS tags are observed, rules are then extracted if the same reordering patterns appear frequently.
@@
 Following is a reordering pattern of a tree rule:\medskip\\
-\texttt{NP ( ADJP JJ NN ) -> JJ NN ADJP}\medskip\\
-The parenthesis in the example represents the hierarchy in the syntax tree.
+\texttt{NP ( ADJP JJ NN ) -> JJ NN ADJP}%\medskip\\
+%The parenthesis in the example represents the hierarchy in the syntax tree.
 The left side of the rule corresponds a tree with the root labeled with \emph{NP} and three children, each labeled with \emph{ADJP}, \emph{JJ} and \emph{NN}.
@@
 
-However, not all these reordering problem of Chinese translation can be solved well by using these reordering rules based either on POS tag sequence or single level of syntax tree.
+However, not all these reordering problems of translating Chinese can be solved well by using these reordering rules based either on POS tag sequence or single level of syntax tree.
 In order to improve the reordering between English and Chinese, we need reordering method that can handle more complicated, unstructural word order change.
@@
 \noindent \texttt{NP ( \textbf{CD}$_0$ NP ( NP ( \textbf{JJ}$_1$ \textbf{NNS}$_2$ ) PP ( \textbf{IN}$_3$ \textbf{NP}$_4$ ) ) ) -> NP IN CD JJ NNS}\medskip \\
-\texttt{or -> 4 3 0 1 2 (with index)}\bigskip
+\texttt{-> 4 3 0 1 2 (alternative with index)}\bigskip
 
-where the POS tags in bold corresponds to words in the leaf nodes of the syntax tree, which are parts that are actually reordered and have a darker gray color in the figure.
+The POS tags in bold corresponds to words in the leaf nodes of the syntax tree, which are parts that are actually reordered and have a darker gray color in the figure.
 The parentheses in the reordering pattern indicate the corresponding hierarchies in the syntax tree.
@@
 
-The results shows increasing scores as we used reordering methods from short rules, long rules, tree rules to MLT rules.
-And better BLEU scores were achieved as we combined the different reordering rules.
+The results shows increasing scores when we used reordering methods from short rules, long rules, tree rules to MLT rules.
+And better BLEU scores were achieved when we combined the different reordering rules.
 The MLT rules achieved better BLEU scores and TER scores in both translation directions, not only when it was used alone, but also it was added to the other reordering rules.

### 2014-09-25 Paper/paper.tex
.

@@
 \usepackage{iwslt14,amssymb,amsmath,epsfig,multirow,spreadtab,array}
+\usepackage[normalem]{ulem}
 \usepackage{tikz}
@@
 \title{Rule-Based Preordering on
-Multiple Syntactic Levels in
-Statistical Machine Translation}
+Multiple Syntactic Levels \\in Statistical Machine Translation}
 
@@
  \makeatother
- \name{{\em Ge Wu, Yuqi Zhang}}
+ \name{{\em Ge Wu, Yuqi Zhang, Alex Waibel}}
 %%%%%%%%%%%%%%% End of required multiple authors changes %%%%%%%%%%%%%%%%%
@@
 Karlsruhe Institute of Technology, Germany \\
-{\small \tt utcur@student.kit.edu, yuqi.zhang@kit.edu}
+{\small \tt utcur@student.kit.edu, yuqi.zhang@kit.edu, alexander.waibel@kit.edu }
 }
@@
 \begin{abstract}
-We propose a novel data-driven rule-based preordering approach, which uses the information of syntax tree and word alignment to reorder the words in source sentences before decoding in a phrase-based SMT system between English and Chinese.
-The preordering algorithm extracts reordering patterns from multiple levels of the syntax trees of the training data and applies the rules on the source sentences in a similar way.
+We propose a novel data-driven rule-based preordering approach, which uses the tree information of multiple syntactic levels.
+This approach extend the tree-based reordering from one level into multiple levels, which has the capability to process more complicated reordering cases.
 We've conducted experiments in English-to-Chinese and Chinese-to-English translation directions.
-Our results show that the approach has led to improved translation quality both when it was applied separately on the baseline or when it was combined with some other reordering approaches.
+Our results show that the approach has led to improved translation quality both when it was applied separately or when it was combined with some other reordering approaches.
 As our reordering approach was used alone, it showed an improvement of $1.61$ in BLEU score in the English-to-Chinese translation direction and an improvement of $2.16$ in BLEU score in the Chinese-to-English translation direction, in comparison with the baseline, which used no word reordering.
 As our preordering approach were combined with the short rule \cite{short}, long rule \cite{long} and tree rule \cite{tree} based preordering approaches, it showed further improvements of up to $0.43$ in BLEU score in the English-to-Chinese translation direction and further improvements of up to $0.3$ in BLEU score in the Chinese-to-English translation direction.
-Through the translations that used our preordering approach, we've also found improvements in syntactic structure.
+Through the translations that used our preordering approach, we've also found many translation examples with improved syntactic structures.
+
+%syntax tree and word alignment to reorder the words in source sentences before decoding in a phrase-based SMT system between English and Chinese.
+The preordering algorithm extracts reordering patterns from multiple levels of the syntax trees of the training data and applies the rules on the source sentences in a similar way.
+
 \end{abstract}
@@
 \section{Introduction}
+\label{in}
 
-Word order is a general issue when we want to translate text from one language to the other.
+Word order is a general issue when we want to translate text from one language to another.
 Different languages normally have different word orders and the difference could be very huge.
@@
 
+The rest of this paper is organized as follows.
+Section~\ref{re} presents a review of related work.
+In Section~\ref{mo}, we point out the problems for translation between English and Chinese and describe the motivation of MLT reordering.
+In Section~\ref{mu}, we introduce the details of the MLT preordering.
+In Section~\ref{ex}, we present the experiment results and evaluation.
+Finally, we conclude this paper in Section~\ref{co}.
+
 \section{Related Work}
+\label{re}
 
@@
 Words can be reordered during the decoding phase by setting a window, which allows the decoder to choose the next word for translation.
-Reordering could also be influenced by the language model, because the language model give probability of how a certain word is likely to follow.
+Reordering could also be influenced by the language model, because the language model gives probability of how a certain word is likely to follow.
 Different language model may give different probability, which further influences the decision made by log-linear model.
@@
 
-However, these approaches which are bases on POS tag sequences or syntax trees are mostly designed for languages like German and are not especially adapted for languages like Chinese.
+However, these approaches which are based on POS tag sequences or syntax trees are mostly designed for languages like German and are not especially adapted for languages like Chinese.
 As Chinese has very different word orders, a reordering approach, which can further explore the syntactic structure of Chinese and utilize this information for reordering, is desirable.
@@
 
+In this paper, we compare our results to the aforementioned rule-based reordering methods and the oracle reordering to get a better overview.
+
 \section{Motivation}
+\label{mo}
 
@@
 
-Some typical problems of word orders between English and Chinese that we've found in the data are as follows:
+Some typical problems of word orders between English and Chinese that we have found are as follows:
 
@@
 This involves the position change of adverbials, relative clauses and preposition phrases during translation.
+Figure~\ref{relative} shows an example of how the position of a relative clause changes
+\begin{figure}
+\input{relative.tikz}
+\caption{Position change of a relative clause}
+\label{relative}
+\end{figure}
 \item \emph{Construction of questions}\\
-The two languages have very different ways to construct questions, which raises word order problems for translating questions.
-\item \emph{Special sentence constructions}\\ For example, \emph{B\^{a}}-construction in Chinese and sentence constructions such as \emph{there be} and inverted negative sentences in English don't have correspondence in the other language in general.
+The two languages have very different ways to construct questions, which raises word order problems for translating questions. Figure~\ref{question} shows word reordering of a question.
+\begin{figure}
+\input{question.tikz}
+\caption{Word reordering of a question}
+\label{question}
+\end{figure}
+\item \emph{Special sentence constructions}\\ For example, \emph{B\^{a}}-construction (\cntext{把字句}) in Chinese and sentence constructions such as \emph{there-be} and inverted negative sentences in English do not have correspondence in the other language in general.
 \item \emph{Long distance word position change}\\
 Word reordering between English and Chinese often involves word shift cross long distance.
+For example, following translation shows that a adverbial clause (underlined) is shifted cross long distance when being translated.\bigskip \\
+\parbox{0.3705\textwidth}{
+I find this very much disturbing \uline{when we are talking about what is going on right and wrong with democracy these days}.\medskip\\
+\cntext{\uline{现在，每当我跟别人讨论我们的民主什么是}}
+\cntext{\uline{对的，什么是错的}我都为此觉得很无力。}
+}
 \end{itemize}
 
-From previous work of others, the following types of reordering rules have been researched:
-
-\begin{itemize}
-\item \emph{Short rules} \cite{short} \\
-Short rules are extracted based on the sequences of adjacent words or their POS tags in sentences from training data.
-Sequences of adjacent words or POS tags are observed, rules are then extracted if the same reordering patterns appear frequently.
-Following is a reordering pattern of a short rule:\medskip\\
-\texttt{WRB MD DT -> DT WRB MD}
-\item \emph{Long rules} \cite{long}\\
-Long rules are specially designed to improve the long distance word reordering for language pairs like English and German.
-The rules are based on POS tags of the text, and use a placeholder ($*$) to represent one or more words.
-Following is a reordering pattern of a long rule:\medskip\\
-\texttt{NN $*$ MD -> $*$ MD NN}
-
-\item \emph{Tree rules} \cite{tree}\\
-While short rules and long rules are based on the flat structure of sentences, tree rules reorder sentences by using information from sentences' syntactic structure.
-The syntax tree and word alignment of the training corpus are used to train the reordering rules.
-The tree rules reorder the words both on the word level and on the constituent level.
-Following is a reordering pattern of a tree rule:\medskip\\
-\texttt{NP ( ADJP JJ NN ) -> JJ NN ADJP}%\medskip\\
-%The parenthesis in the example represents the hierarchy in the syntax tree.
-The left side of the rule corresponds a tree with the root labeled with \emph{NP} and three children, each labeled with \emph{ADJP}, \emph{JJ} and \emph{NN}.
-\end{itemize}
-
-However, not all these reordering problems of translating Chinese can be solved well by using these reordering rules based either on POS tag sequence or single level of syntax tree.
-In order to improve the reordering between English and Chinese, we need reordering method that can handle more complicated, unstructural word order change.
-Inspired by the ideas of reordering on syntax tree and hierarchical phrases, we created the MLT reordering, which reorders words based on multiple syntactic levels and can handle long distance word position change and complicated word position change very well.
+Following the analysis above, in order to improve the reordering between English and Chinese, we need reordering method that can handle more complicated, unstructural word order change.
+Inspired by the ideas of reordering on syntax tree and hierarchical phrases, we created the Multiple-Level-Tree(MLT) reordering, which reorders words based on multiple syntactic levels and can handle long distance word position change and complicated word position change very well.
 
 \section{Multi-Level-Tree Reordering}
+\label{mu}
 
-Our preordering method is based on reordering rules.
+Our preordering method is based on automatically learned reordering rules.
 Reordering rules show how sentences should be reordered in source language before translation.
@@
 A word lattice contains all the reordering possibilities of a source sentence and is further passed to the decoder for translation.
-The preordering system could be illustrated as figure~\ref{prereordering}.
+The preordering system could be illustrated as Figure~\ref{prereordering}.
 
@@
 \centering
+\tikzset{every picture/.style={scale=0.8}}%
 \input{prereordering.tikz}
@@
 These nodes that are used for detecting the reordering pattern are colored gray and have an italic font.
+Especially, the nodes with dark gray are the lowest ones among such nodes, which represent constituents that are actually reordered through the reordering rules.
 The leaf nodes in the syntax tree indicate words in the sentence, which has rectangle shape with angular corners.
 
-According to the alignment information with the corresponding Chinese translation, the node labeled with \emph{NP} is moved forward to the first place in the translation and the node labeled with \emph{IN of} is moved forward to the second place in translation.
-So from the root node with a search depth $3$, the following reordering pattern can be found:\bigskip
+According to the alignment information with the corresponding Chinese translation, the node labeled with \emph{NP} is moved forward to the first place in the translation and the node labeled with \emph{IN-of} is moved forward to the second place in translation.
+This reordering cannot be handled with one-level tree-based reordering, but in MLT, from the root node with a search depth of three, the following reordering pattern can be found:\bigskip
 
-\noindent \texttt{NP ( \textbf{CD}$_0$ NP ( NP ( \textbf{JJ}$_1$ \textbf{NNS}$_2$ ) PP ( \textbf{IN}$_3$ \textbf{NP}$_4$ ) ) ) -> NP IN CD JJ NNS}\medskip \\
+\noindent \texttt{NP(\textbf{CD}$_0$ NP(NP(\textbf{JJ}$_1$ \textbf{NNS}$_2$)PP(\textbf{IN}$_3$ \textbf{NP}$_4$)))}\medskip\\
+\texttt{-> NP IN CD JJ NNS}\\
 \texttt{-> 4 3 0 1 2 (alternative with index)}\bigskip
 
-The POS tags in bold corresponds to words in the leaf nodes of the syntax tree, which are parts that are actually reordered and have a darker gray color in the figure.
+The POS tags in bold corresponds to nodes with dark gray in Figure~\ref{unstructured}, which presents constituents that are actually reordered.
 The parentheses in the reordering pattern indicate the corresponding hierarchies in the syntax tree.
@@
 
-\begin{figure}
+\begin{figure}[ht]
 \centering
+%\tikzset{every picture/.style={scale=0.8}}%
 \input{unstructured.tikz}
@@
 
-In order to find as much information for reordering as possible.
-The algorithm of rule extraction detects the reordering patterns from all nodes in the syntax tree and it goes downwards for any number of hierarchies, until it reaches the lowest hierarchy in the subtrees.
+In order to find as much information for reordering as possible, the algorithm of rule extraction detects the reordering patterns from all nodes in the syntax tree and it goes downwards for any number of hierarchies, until it reaches the lowest hierarchy in the subtrees.
 
@@
 
-\begin{figure}
+\begin{figure}[ht]
 \centering
@@
 
-Figure~\ref{extract} shows a phrase to be translated, together with its syntax tree and word alignment of parallel text.
-The leaf nodes are underlined and indexed according to the order they appear in the left side of the patterns.
-The index sequences on the right side of the patterns indicate the reordering.
-In this example, we can find the following reordering patterns:\bigskip
+Figure~\ref{extract} shows a phrase to be translated, together with its syntax tree and word alignment of parallel text. In this example, we can find the following reordering patterns:\bigskip
 
 \noindent From node $1$:\\
-\texttt{NP ( \textbf{NP} \textbf{PP} ) -> 1 0} \hfill [1 level]\hphantom{s}\\
-\texttt{NP ( NP ( \textbf{JJ} \textbf{NNS} ) PP ( \textbf{IN} \textbf{NP} ) ) -> 3 2 0 1} \hfill [2 levels]\\
-\texttt{NP ( NP ( \textbf{JJ} \textbf{NNS} ) PP ( \textbf{IN} NP ( \textbf{JJ} \textbf{NNS} ) ) ) -> 3 4 2 0 1} \hfill [3 levels]\medskip
+\texttt{NP(\textbf{NP} \textbf{PP})->1 0} \hfill [1 level]\hphantom{s}\\
+\texttt{NP(NP(\textbf{JJ} \textbf{NNS})PP(\textbf{IN} \textbf{NP}))->3 2 0 1} \hfill [2 levels]\\
+\texttt{NP(NP(\textbf{JJ} \textbf{NNS})PP(\textbf{IN} NP(\textbf{JJ} \textbf{NNS})))-> \\ 3 4 2 0 1} \hfill [3 levels]\medskip
 
 \noindent From node $3$:\\
-\texttt{PP ( \textbf{IN} \textbf{NP} ) -> 1 0} \hfill [1 level]\hphantom{s}\\
-\texttt{PP ( \textbf{IN} NP ( \textbf{JJ} \textbf{NNS} ) ) -> 1 2 0} \hfill [2 levels]\bigskip
+\texttt{PP(\textbf{IN} \textbf{NP})->1 0} \hfill [1 level]\hphantom{s}\\
+\texttt{PP(\textbf{IN} NP(\textbf{JJ} \textbf{NNS}))->1 2 0} \hfill [2 levels]\bigskip
 
@@
 The syntax tree is traversed by DFS as the same in rule extraction.
-But from the root of each subtree, it's scanned with depth limit from its maximal levels, i.e.
+But from the root of each subtree, it has scanned with depth limit from its maximal levels, i.e.
 its depth, to $1$.
-As it turns out, any rule can be applied for a subtree at some level, a new path for this reordering will be added to the word lattice for decoding.
-As long as rules can be applied on a subtree for a certain depth, the rules are applied and the search for rule application on this subtree stops, and the search on the next subtree continues.
+As it turns out that any rule can be applied for a subtree at some level, a new path for this reordering will be added to the word lattice for decoding.
+As long as rules can be applied on a subtree for a certain depth, the search for rule application on this subtree stops, and the search on the next subtree continues.
 
-The reason for this is to prevent duplicate reorderings due to application of nested rules, which has overlapped effect with each other.
+The reason for this is to prevent duplicate reorderings due to application of nested rules, which have overlapped effect with each other.
 These rules are normally patterns that are generated on the same subtree, but with different number of levels, which has different generalization effect on the same range of words in the text.
-For example, the following patterns can be detected from the syntax tree in figure~\ref{extract}:\bigskip
+For example, the following patterns can be detected from the syntax tree in Figure~\ref{extract}:\bigskip
 
-\noindent \texttt{PP ( \textbf{IN} \textbf{NP} ) -> 1 0}\\
-\texttt{PP ( \textbf{IN} NP ( \textbf{JJ} \textbf{NNS} ) ) -> 1 2 0}\bigskip
+\noindent \texttt{PP(\textbf{IN} \textbf{NP}) -> 1 0}\\
+\texttt{PP(\textbf{IN} NP(\textbf{JJ} \textbf{NNS})) -> 1 2 0}\bigskip
 
-Both patterns are detected from the same node, but the second pattern is detected by retrieving the nodes one level deeper and it's more concrete.
+Both patterns are detected from the same node, but the second pattern is detected by retrieving the nodes one level deeper and it is more concrete.
 So the first pattern can be seen as a generalization of the second pattern.
@@
 Because subtrees are checked from the highest number of levels in rule application, the more concrete rule is applied first.
-Because the more concrete rule fits the detected pattern better and contains more details of reordering, so it may be more suitable for rule application.
+Since the more concrete rule fits the detected pattern better and contains more details of reordering, so it may be more suitable for rule application.
 In this example, the second rule is applied rather than the first rule.
@@
 This is done by training the different types of rules separately and applying them on the monotone path of the sentence independently.
-They generate different paths in the word lattice.
+All the generated different paths are compressed in the word lattice.
 
 \section{Experiments}
+\label{ex}
 
-We've conducted experiments on both English-to-Chinese and Chinese-to-English translation directions to get a better overview of the MLT reordering's effect.
+We have conducted experiments on both English-to-Chinese and Chinese-to-English translation directions to get a better overview of the MLT reordering's effect.
 In the experiments, the MLT reordering rules are also combined with other reordering rules that are introduced before, in order to show the improvement achieved by our approach.
@@
 In order to evaluate the potential of word reordering, we also used oracle reordering in the experiments.
-Oracle reordering is considered to be an optimally reordered sentence as input to the SMT system and do not allow additional reordering during decoding.\cite{combine} The oracle reordering is created by using the permutation of source sentences, which is extracted from the word alignment between the source text and reference.\cite{birch2}
+Oracle reordering is considered to be an optimally reordered sentence as input to the SMT system and do not allow additional reordering during decoding \cite{combine}.
+The oracle reordering is created by using the permutation of source sentences, which is extracted from the word alignment between the source text and reference \cite{birch2}.
 
@@
 
-We performed experiments with or without different reordering methods covering the English-to-Chinese translation direction.
+We performed experiments with and without different reordering methods covering the English-to-Chinese translation direction.
 The reordering methods included our MLT reordering approach and the other reordering approaches with short rules, long rules and tree rules.
@@
 Table~\ref{tenw} shows the BLEU scores, absolute improvements of BLEU scores and TER scores for configurations with different reordering methods.
-The table consist of $2$ sections.
+The table consists of $2$ sections.
 the first row of the top section shows results of the baseline, which used no preordering at all.
-In the following rows of the top section, different types of reordering rules are combined gradually, with each type per row, and the results are showed.
-For example, the row with \emph{$+$MLT} Rules presents the configuration with all the rule types including MLT rules and all the other rules in the rows above.
+In the following rows of the top section, different types of reordering rules are combined gradually, with each type per row.
+For example, the row with \emph{$+$MLT Rules} presents the configuration with all the rule types including MLT rules and all the other rules in the rows above.
 All improvements are absolute improvements of BLEU scores in comparison to the baseline.
-Each row with a certain reordering type presents all the different variations of this type and the best score under these configurations are shown.
+Each row with a certain reordering type presents all the different variations of this type and the best score under these configurations is shown.
 For example, long rules include the left rules and right rules, and the tree rules include the partial rules and recursive application.
@@
 
-The experiments for Chinese-to-English systems had a similar setup as described in the last section.
+The experiments for Chinese-to-English systems have a similar setup as described in the last section.
 The parallel data used in the English-to-Chinese system was also used in this experiment by switching the source language and the target language.
@@
 The test data had three English references for evaluating the results instead of one as in the previous system.
-The data used are summarized in table~\ref{dzhen2}.
+The data used are summarized in Table~\ref{dzhen2}.
 
@@
 Table~\ref{tzhen2} shows the results for configurations with different reordering methods for the Chinese-to-English translation.
-The table can be interpreted in the same manner as table~\ref{tenw} in the previous section.
+The table can be interpreted in the same manner as Table~\ref{tenw} in the previous section.
 
@@
 
-We've also found improvements in the sentence structure.
-Table~\ref{te} shows some translation examples in both translation directions.
+We have also found improvements in the sentence structure.
+Table~\ref{t1} and Table~\ref{t2} shows some translation examples in both translation directions.
 Sections are separated by double lines in the table.
 Each section of this table shows one translation example with the source sentence (\emph{source}), translation without using MLT reordering (\emph{no MLT}), translation with MLT reordering (\emph{MLT}) and the reference (\emph{reference}).
+\emph{Glossary} for the source sentences in translation examples from English to Chinese is also added for understanding.
 The translation without using MLT reordering comes from the configuration with highest BLEU score that didn't use MLT reordering.
@@
 From the examples, we can clearly see the improvements in sentence structure.
+
+% Each word or group of hyphenated words in the glossary corresponds a Chinese character or a group of Chinese characters that are not separated with space in the source sentence with the same order.
+
+\begin{table*}
+\centering
+\begin{tabular}{|l|m{0.7\textwidth}|} \hline
+Source & \cntext{陈至立 说 , 古巴 是 拉美 和 加勒比 地区 有 重要 影响 的 国家 。}
+\\ \hline
+Glossary & chen-zhili said , cuba is latin-american and caribbean region has great influence of country .
+\\ \hline
+No MLT & chen zhili said : cuba is the latin america and the caribbean region has an important influence on the state .
+\\ \hline
+MLT & chen zhili said : cuba is a country of important influence latin america and the caribbean region .
+\\ \hline
+Reference & chen zhili said that cuba is a country of great influence in the latin american and caribbean region .
+\\ \hline \hline
+
+Source & \cntext{近年 来 , 两 国 教育 交流 日益 密切 , 人员 来往 频繁 。}
+\\ \hline
+Glossary & recent-years in, two countries educational exchange increasingly close , personnel visits frequent .
+\\ \hline
+no MLT & in recent years , the two countries education have been increasingly close exchanges and personnel contacts have been frequent .
+\\ \hline
+MLT & in recent years , the educational exchanges between the two countries have become increasingly frequent , and have had frequent contacts .
+\\ \hline
+Reference & in recent years , the educational exchange between the two countries has become increasingly close with frequent personnel visits .
+\\ \hline
+\end{tabular}
+\caption{Examples of translations from Chinese to English}
+\label{t1}
+\end{table*}
 
@@
 %? add more examples?
-Reference & \cntext{达赖 喇嘛 将 在 本 月 前往 华盛顿 访问 。} \\ \hline \hline
-Source & \cntext{陈至立 说 , 古巴 是 拉美 和 加勒比 地区 有 重要 影响 的 国家 。}
-\\ \hline
-No MLT & chen zhili said : cuba is the latin america and the caribbean region has an important influence on the state .
-\\ \hline
-MLT & chen zhili said : cuba is a country of important influence latin america and the caribbean region .
-\\ \hline
-Reference & chen zhili said that cuba is a country of great influence in the latin american and caribbean region .
-\\ \hline \hline
-
-Source & \cntext{近年 来 , 两 国 教育 交流 日益 密切 , 人员 来往 频繁 。}
-\\ \hline
-no MLT & in recent years , the two countries education have been increasingly close exchanges and personnel contacts have been frequent .
-\\ \hline
-MLT & in recent years , the educational exchanges between the two countries have become increasingly frequent , and have had frequent contacts .
-\\ \hline
-Reference & in recent years , the educational exchange between the two countries has become increasingly close with frequent personnel visits .
-\\ \hline
-
+Reference & \cntext{达赖 喇嘛 将 在 本 月 前往 华盛顿 访问 。} \\ \hline
 \end{tabular}
-\caption{Examples of translations}
-\label{te}
+\caption{Examples of translations from English to Chinese}
+\label{t2}
 \end{table*}
-
-However, by taking a close look at the gap between the scores of oracle reordering and the best scores achieved by MLT reordering, we can also see, there's still potential for improvements of translation between English and Chinese through better reordering methods.
 
@@
 \section{Conclusions}
+\label{co}
 
-We've present a new preordering approach for translation between English and Chinese.
-The algorithm detects and applies reordering rules uses information of word alignment and multiple syntactic levels in the syntax tree to reorder the source sentences.
+We have presented a new preordering approach for translation
+between English and Chinese.
+The algorithm detects and applies reordering rules by using information of multiple syntactic levels in the syntax tree and word alignment to reorder the source sentences.
 Reordering patterns are detected by checking if the nested tag sequences in subtrees with any number of search levels have clearly new orders in the aligned text in the target language.
 
-We've conducted experiments in both translation directions between English and Chinese with different SMT configurations.
-From the results we can see the BLEU scores was improved no matter when we applied the SMT reordering method to the baseline directly or when we combined it with the other reordering methods we introduced before, i.e.
+We have conducted experiments in both translation directions between English and Chinese with different SMT configurations.
+From the results we can see the BLEU scores were improved no matter when we applied the SMT reordering method to the baseline directly or when we combined it with the other reordering methods, i.e.
 short rules, long rules and tree rules based reordering methods.
 
-When our approach was applied alone, it achieved an BLEU score improvement of $1.61$ in the English-to-Chinese translation direction, and an BLEU score improvement of $2.16$ in the Chinese-to-English translation direction.
+%When our approach was applied alone, it achieved an BLEU score improvement of $1.61$ in the English-to-Chinese translation direction, and an BLEU score improvement of $2.16$ in the Chinese-to-English translation direction.
 
-When our approach was combined with the short rules, long rules and tree rules based reordering methods, further improvements were achieved for both translation direction.
+%When our approach was combined with the short rules, long rules and tree rules based reordering methods, further improvements were achieved for both translation directions.
 Our approach improved the BLEU score further by $0.43$ in the English-to-Chinese translation direction and by $0.30$ in the Chinese-to-English translation direction.
@@
 Besides the improvement in BLEU scores, our preordering approach also showed improvement in the sentence structure of the translation.
+Considering sentences that have complicated structure only make up a small portion of the data, even a small improvement in the result can mean a big improvement in translating these complicated sentences.
+
+By taking a close look at the gap between the scores of oracle reordering and the best scores achieved by MLT reordering, we can also see, there's still potential for improvements of translation between English and Chinese through better reordering methods.
 

### 2014-09-25 Paper/clear.sh

@@ -1,0 +1,8 @@
+rm *.aux
+rm *.lof
+rm *.log
+rm *.lot
+rm *.toc
+rm *.bbl
+rm *.blg
+rm *.pdf

### 2014-09-25 Paper/paper.tex
.

@@
  \makeatother
- \name{{\em Ge Wu, Yuqi Zhang, Alex Waibel}}
+% \name{{\em Ge Wu, Yuqi Zhang, Alex Waibel}}
 %%%%%%%%%%%%%%% End of required multiple authors changes %%%%%%%%%%%%%%%%%
 
-\address{Institute for Anthropomatics \\
-Karlsruhe Institute of Technology, Germany \\
-{\small \tt utcur@student.kit.edu, yuqi.zhang@kit.edu, alexander.waibel@kit.edu }
-}
-%
+%\address{Institute for Anthropomatics \\
+%Karlsruhe Institute of Technology, Germany \\
+%{\small \tt utcur@student.kit.edu, yuqi.zhang@kit.edu, alexander.waibel@kit.edu }
+%}
+
 \begin{document}
@@
 In Section~\ref{mo}, we point out the problems for translation between English and Chinese and describe the motivation of MLT reordering.
-In Section~\ref{mu}, we introduce the details of the MLT preordering.
-In Section~\ref{ex}, we present the experiment results and evaluation.
+In Section~\ref{mu}, we introduce the details of the MLT reordering.
+In Section~\ref{ex}, we present the experimental results and evaluation.
 Finally, we conclude this paper in Section~\ref{co}.
@@
 These nodes that are used for detecting the reordering pattern are colored gray and have an italic font.
-Especially, the nodes with dark gray are the lowest ones among such nodes, which represent constituents that are actually reordered through the reordering rules.
+The nodes with dark gray are the lowest ones among such nodes, which represent constituents that are actually reordered through the reordering rules.
 The leaf nodes in the syntax tree indicate words in the sentence, which has rectangle shape with angular corners.
@@
 Oracle reordering is considered to be an optimally reordered sentence as input to the SMT system and do not allow additional reordering during decoding \cite{combine}.
-The oracle reordering is created by using the permutation of source sentences, which is extracted from the word alignment between the source text and reference \cite{birch2}.
-
-Because oracle reordering is considered as an optimally reordering, we can use it as input of the SMT system and the scores are the optimal results that can be achieved by word reordering, from which we can evaluate the potential of reordering methods.
+So we can use it as input of the SMT system and the scores are the optimal results that can be achieved by word reordering, from which we can evaluate the potential of reordering methods.
 
@@
 Each section of this table shows one translation example with the source sentence (\emph{source}), translation without using MLT reordering (\emph{no MLT}), translation with MLT reordering (\emph{MLT}) and the reference (\emph{reference}).
-\emph{Glossary} for the source sentences in translation examples from English to Chinese is also added for understanding.
+\emph{Glossary} for the source sentences or references in Chinese is also added as word for word translation.
+Each word or group of hyphenated words in the glossary corresponds a Chinese character or a group of Chinese characters that are not separated with space.
+A placeholder $\Box$ is used to replace words that are difficult to translate, which play grammatical roles generally.
 The translation without using MLT reordering comes from the configuration with highest BLEU score that didn't use MLT reordering.
@@
 \\ \hline
-Glossary & chen-zhili said , cuba is latin-american and caribbean region has great influence of country .
+Glossary & chen-zhili said , cuba is latin-american and caribbean region has great influence $\Box$ country .
 \\ \hline
@@
 MLT & \cntext{胡锦涛 还 对 中国 迂难者 表示 哀悼 , 向 迂难者 家属 表示 诚挚 的 慰问 。} \\ \hline 
-Reference & \cntext{胡锦涛 还 对 中方 不幸 遇难 人员 表示 深切 的 哀悼 , 并 向 遇难 着 的 亲属 致以 诚挚 的 慰问 。} \\ \hline \hline
+Reference & \cntext{胡锦涛 还 对 中方 不幸 遇难 人员 表示 深切 的 哀悼 , 并 向 遇难者 的 亲属 致以 诚挚 的 慰问 。} \\ \hline
+Glossary & hu-jintao also on chinese unfortunately killed people extended deep $\Box$ condolences , and to bereaved 's families expressed sincere $\Box$ sympathy .
+\\ \hline \hline
 Source & satisfying personal interests and expanding knowledge are also major reasons why hourly work appeals to people .\\ \hline
@@
 MLT & \cntext{满足 个人 利益 和 扩大 知识 也 是 为什么 学生 工作 吸引 人 的 主要 原因 。} \\ \hline 
-Reference & \cntext{满足 个人 兴趣 , 扩大 自己 的 知识面 也 是 兼职 小时 工 受 青睐 的 一 个 重要 原因 。} \\ \hline \hline
+Reference & \cntext{满足 个人 兴趣 , 扩大 自己 的 知识面 也 是 兼职 小时 工 受 青睐 的 一 个 重要 原因 。}  \\ \hline
+Glossary & satisfying personal interests , expanding own $\Box$ knowledge also are part-time hourly work is favored $\Box$ one $\Box$ major reason .
+\\ \hline \hline
 
@@
 Reference & \cntext{达赖 喇嘛 将 在 本 月 前往 华盛顿 访问 。} \\ \hline
+Glossary & dalai lama will in this month go-to washington visit .
+\\ \hline
 \end{tabular}

### 2014-09-25 Paper/paper.tex
.

@@
  \makeatother
-% \name{{\em Ge Wu, Yuqi Zhang, Alex Waibel}}
+% \name{{\em Ge Wu, Yuqi Zhang, Alexander Waibel}}
 %%%%%%%%%%%%%%% End of required multiple authors changes %%%%%%%%%%%%%%%%%
@@
 We have also found improvements in the sentence structure.
-Table~\ref{t1} and Table~\ref{t2} shows some translation examples in both translation directions.
+Table~\ref{t1} and Table~\ref{t2} show some translation examples in both translation directions.
 Sections are separated by double lines in the table.
@@
 Besides the improvement in BLEU scores, our preordering approach also showed improvement in the sentence structure of the translation.
-Considering sentences that have complicated structure only make up a small portion of the data, even a small improvement in the result can mean a big improvement in translating these complicated sentences.
+Considering sentences that have complicated structure only make up a small part of the data, even a small improvement in the result can mean a big improvement in translating these complicated sentences.
 

### 2014-09-25 Paper/clear.sh

@@ -1,3 +1,5 @@
+rm *.dvi
+rm *.ps
 rm *.aux
 rm *.lof
 rm *.log

### 2014-09-26 Paper/paper.tex
.

@@
 This approach extend the tree-based reordering from one level into multiple levels, which has the capability to process more complicated reordering cases.
-We've conducted experiments in English-to-Chinese and Chinese-to-English translation directions.
+We have conducted experiments in English-to-Chinese and Chinese-to-English translation directions.
 Our results show that the approach has led to improved translation quality both when it was applied separately or when it was combined with some other reordering approaches.
@@
 As our preordering approach were combined with the short rule \cite{short}, long rule \cite{long} and tree rule \cite{tree} based preordering approaches, it showed further improvements of up to $0.43$ in BLEU score in the English-to-Chinese translation direction and further improvements of up to $0.3$ in BLEU score in the Chinese-to-English translation direction.
-Through the translations that used our preordering approach, we've also found many translation examples with improved syntactic structures.
+Through the translations that used our preordering approach, we have also found many translation examples with improved syntactic structures.
 
@@
 Or an additional reordering model is used in the log-linear model for word reordering.
-However, these methods may have some disadvantages, such as some don't handle long-distance reordering, some don't handle unstructured reordering and some are rather time-consuming.
+However, these methods may have some disadvantages, such as some do not handle long-distance reordering, some do not handle unstructured reordering and some are rather time-consuming.
 
@@
 Thus, a word-for-word translation between English and Chinese is often unnatural or difficult to understand.
-Each of them has some sentence patterns that don't exist or rarely used in the other.
+Each of them has some sentence patterns that do not exist or rarely used in the other.
 In Chinese, a modifier is often put before the part that it modifies.
 While in English, it is very common that the modifier is put after the part that it modifies.
-Besides, English sentences with a lot of long clauses may be more suitable to translate into several Chinese sentences, because in Chinese people don't tend to use long clauses in general.
+Besides, English sentences with a lot of long clauses may be more suitable to translate into several Chinese sentences, because in Chinese people do not tend to use long clauses in general.
 
@@
 A placeholder $\Box$ is used to replace words that are difficult to translate, which play grammatical roles generally.
-The translation without using MLT reordering comes from the configuration with highest BLEU score that didn't use MLT reordering.
+The translation without using MLT reordering comes from the configuration with highest BLEU score that did not use MLT reordering.
 And the translation with MLT reordering comes from the configuration with highest BLEU score that used MLT reordering.
@@
 
-By taking a close look at the gap between the scores of oracle reordering and the best scores achieved by MLT reordering, we can also see, there's still potential for improvements of translation between English and Chinese through better reordering methods.
+By taking a close look at the gap between the scores of oracle reordering and the best scores achieved by MLT reordering, we can also see, there is still potential for improvements of translation between English and Chinese through better reordering methods.
 

### 2014-11-14 Paper/paper.tex
.
corrected

@@
 
-Most state-of-the-art phrase-based SMT systems use language model, phrase table or decoder to adjust the word order.
-Or an additional reordering model is used in the log-linear model for word reordering.
-However, these methods may have some disadvantages, such as some do not handle long-distance reordering, some do not handle unstructured reordering and some are rather time-consuming.
+The decoder in phrase-based SMT systems is guided by language model, phrase table and reordering models, which makes word reordering possible.
+However, it may have some disadvantages, such as it can't handle long-distance reordering or unstructured reordering properly or it may be rather time-consuming.
 
@@
 Afterwards, Herrmann et al.
-2013 \cite{tree} introduced a new approach to reorder the words based on syntax tree, which leads to further improvements on translation quality.
-The algorithm takes syntactic structure of the sentences into account and extract the rules from the syntax tree by detecting the reordering of child sequences.
-It also has the variant based only on part of the child sequences which is suitable for language with flat syntactic structure such as German.
+2013 \cite{tree} introduced a new approach to reorder the words based on syntax tree, which led to further improvements on translation quality.
+The algorithm takes the syntactic structure of the source sentence into account and extract the rules from the syntax tree by detecting the reordering of child sequences.
+It is also possible to compute reorderings only based on part of the child sequences, which is suitable for language with flat syntactic structures such as German \cite{combine}.
 
-However, these approaches which are based on POS tag sequences or syntax trees are mostly designed for languages like German and are not especially adapted for languages like Chinese.
-As Chinese has very different word orders, a reordering approach, which can further explore the syntactic structure of Chinese and utilize this information for reordering, is desirable.
+However, these approaches which are based on POS tag sequences or syntax trees may not fully explore the syntactic aspect of Chinese.
+As Chinese has very different word orders, a reordering approach, which can further explore the hierarchical structure of Chinese and utilize this information for reordering, may further improve the translation quality.
 
-The hierarchical phrase-based translation model \cite{hier} is especially suitable for Chinese translation, and provide very good translation results.
+The hierarchical phrase-based translation model \cite{hier} is especially suitable for translation into Chinese, and delivers very good translation results.
 It extracts hierarchical rules by using information of the syntactic structure.
@@
 Sometimes it is very hard to find corresponding words in the other language.
-For example, some prepositions in Chinese have very different usage than those prepositions in English.
+For example, some prepositions in Chinese have very different usage than the corresponding prepositions in English.
 Also the continuous writing of Chinese without spaces makes this problem more severe, since word boundaries are not always so clear in Chinese.
@@
 
-Following the analysis above, in order to improve the reordering between English and Chinese, we need reordering method that can handle more complicated, unstructural word order change.
+Following the analysis above, we can see the word reordering between English and Chinese is very unstructural, because it involves word movement between different word groups or syntactic hierarchies in the source language.
+In order to improve the reordering, we need methods that can handle more complicated, unstructural word order change.
 Inspired by the ideas of reordering on syntax tree and hierarchical phrases, we created the Multiple-Level-Tree(MLT) reordering, which reorders words based on multiple syntactic levels and can handle long distance word position change and complicated word position change very well.
@@
 A word lattice contains all the reordering possibilities of a source sentence and is further passed to the decoder for translation.
-The preordering system could be illustrated as Figure~\ref{prereordering}.
+The preordering system is illustrated as Figure~\ref{prereordering}.
 
@@
 The parentheses in the reordering pattern indicate the corresponding hierarchies in the syntax tree.
-The reordering can be alternatively represented with index, which is the actual internal representation to avoid ambiguity caused by POS tags with the same name and we use this representation throughout this paper.
+The reordering can be alternatively represented with indices, which is the actual internal representation to avoid ambiguity caused by POS tags with the same name and we use this representation throughout this paper.
 
@@
 The detected word position changes are checked for their validity for reordering rules.
-A valid reordering pattern should both has actual word reordering and clearly distinguishable new order on the side of the target language, i.e.
+A valid reordering pattern should both have actual word reordering and clearly distinguishable new order on the side of the target language, i.e.
 no collision of aligned ranges on the target side.
@@
 \end{tabular}
-\caption{Data details in English-to-Chinese system}
+\caption{Corpus statistics in the English-to-Chinese system}
 \label{denw}
@@
 \end{spreadtab}
-\caption{Result overview of English-to-Chinese system}
+\caption{Result overview of the English-to-Chinese system}
 \label{tenw}
@@
 \end{tabular}
-\caption{Data details in Chinese-to-English system}
+\caption{Corpus statistics in the Chinese-to-English system}
 \label{dzhen2}
@@
 \end{spreadtab}
-\caption{Result overview of Chinese-to-English systems}
+\caption{Result overview of the Chinese-to-English systems}
 \label{tzhen2}
@@
 Each word or group of hyphenated words in the glossary corresponds a Chinese character or a group of Chinese characters that are not separated with space.
-A placeholder $\Box$ is used to replace words that are difficult to translate, which play grammatical roles generally.
+A placeholder $\Box$ is used to replace words that are difficult to translate, which play grammatical roles in general.
 The translation without using MLT reordering comes from the configuration with highest BLEU score that did not use MLT reordering.
@@
 
+\section{Acknowledgments}
+\label{Acknowledgments}
+The authors gratefully acknowledge the support by an \mbox{interACT} student exchange scholarship.
+The research leading to these results has received funding from the European Union $7$th Framework Programme (FP$7$/$2007$-$2013$) under grant agreement No.
+$287658$.
+
 \bibliographystyle{myieeetr}

### 2014-11-14 Paper/paper.tex
corrected2

@@
 The decoder in phrase-based SMT systems is guided by language model, phrase table and reordering models, which makes word reordering possible.
-However, it may have some disadvantages, such as it can't handle long-distance reordering or unstructured reordering properly or it may be rather time-consuming.
+However, it may have some disadvantages, such as it can't handle long-distance reordering or unstructured reordering properly, or it may be rather time-consuming.
 
@@
 
-Following the analysis above, we can see the word reordering between English and Chinese is very unstructural, because it involves word movement between different word groups or syntactic hierarchies in the source language.
+Following the analysis above, we can see the word reordering between English and Chinese is very unstructural, because it involves word position changes between different word groups and syntactic hierarchies in the source language.
 In order to improve the reordering, we need methods that can handle more complicated, unstructural word order change.
